---
title: "Baltimore Community Data Science Collaboration, ToolBank Community and Economic Impact Survey Analysis"
author: "Analysis by: Charlotte Clapham, Tianxu Chen, Haley Farrie"
date: "2023-12-14"
output:
  html_document:
    toc: true
---
# Overview
The following report outlines the findings from a survey of ToolBank member organizations regarding their attitudes, economic and community outcomes as a result of utilizing the ToolBank tool lending service. The survey was developed by the ToolBank with support from the Johns Hopkins Baltimore Community Data Science class based upon the results of a pilot survey to high-frequency ToolBank member organizations. The survey contained 25 response fields and was available for members to complete from November 9th 2023 to November 17th 2023. ToolBank members were incentivized to participate by receiving a $25 tool credit for each completed survey, with the the first ten survey responses receiving an additional $25 tool credit. Multiple responses per organization were encouraged to allow for a diversity of experiences to be captured and each additional response per organization was provided a credit of an additional $10. The following sections outline the key findings from the survey; general sentiment stratified by years with the member organization, size of the member organization, and minority status of the member organization; the economic and community impact of the ToolBank, as indicated by respondents; and the impact of the ToolBank on Community Based Organizations' self-reported fundraising capacity. The full project repository is available here: https://github.com/jhudsl/BCDS_ToolBank_2023.git. 

# Section 1: Key Findings
- 100% of respondents strongly agreed (93.3%) or agreed (6.7%) that the ToolBank positively impacts their CBO 
- 100% of respondents strongly agreed (93.3%) or agreed (6.7%) that the ToolBank reduced costs related to purchasing and renting tools and equipment
- 88.9% of the survey respondents reported to at least one of the minority service or leadership criteria. 
- Events got impacted by the TB mainly through their quality (77.8%), consistency (66.7%), and quantity (55.6%)
- The most prominent types of events the toolbank supports are community building (84.4%) and service projects (75.6%)
- For the past year, half of the respondents reported that at least 1/3 (35%) of their events would have been impossible without the help of the TB
- For the past year, half of the respondents reported that at least 150 of their constituents (volunteers, members, and event attendees) would have been negatively impacted without the help of the TB

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, include=FALSE, purl=FALSE}
library(knitr)
opts_chunk$set(comment = "")
```

```{r, include=FALSE}
library(tidyr)
library(tidyverse)
library(googlesheets4)
library(ggplot2)
library(htmlTable)
```

```{r eval=FALSE, include = F}
# Prompts a browser pop-up
gs4_auth(email = TRUE)
```
```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
# Once set up, you can automate this process by passing your email
#gs4_auth(email = "karinchen737@gmail.com")
#gs4_auth(email = "chclapham@gmail.com")
#gs4_auth(email = "haley.farrie@gmail.com")
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#Read in data with the googlesheets4 package {.smaller}
sheet_url <- 
  "https://docs.google.com/spreadsheets/d/1W5kgOFSJux4lqpwqwJ_h9tJnd5oTY3-wBs57cpkyM3U/edit#gid=1386397630"
sheet_dat_1 <- read_sheet(sheet_url)
head(sheet_dat_1)
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include = F}
#2. Read in gross receipts data
sheet_gr_url = "https://docs.google.com/spreadsheets/d/1W5kgOFSJux4lqpwqwJ_h9tJnd5oTY3-wBs57cpkyM3U/edit#gid=1036871075"
data_gr <- read_sheet(sheet_gr_url, sheet = "Sheet1")
colnames(data_gr) = c("timestamp", "cbo_name", "cbo_gr", "cbo_size", "comment")
head(data_gr)
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
# delete Noah's test response
# also delete the "Please specify:" question after receiving the first response, so we want to delete the corresponding column
data = sheet_dat_1[sheet_dat_1$`Name of your current organization` != "Baltimore ToolBank", 
                   !names(sheet_dat_1) %in% c("Please specify:")]
head(data)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE,include=F}
# Change column names to variables
varlist = c("timestamp","di_org", "di_orgyearsworked", "di_mled", "att_purtool", "att_strtool", "att_redtime", "att_evquality", "att_posimpact", "att_mostimpact", "eco_purchase", "eco_storage", "eco_maintain", "eco_totalcost", "eco_events", "eco_nothost", "eco_constit", "ci_exaccomp", "ci_cutfund", "ci_otr", "ci_staff", "ci_project", "ci_evimpact", "eve_type", "eve_fundraise", "eve_fundraise_p")

colnames(data) = varlist
str(data)
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE,include=F}
#Change multiple choice answer into numbers
# Question: how long have you worked with this organization
# variable: di_orgyearsworked; choice: 1 - 0-2 years; 2 - 3-5 years; 3 - More than 5 years

data$di_orgyearsworked = ifelse(data$di_orgyearsworked == "0-2 years", 1,
                                ifelse(data$di_orgyearsworked == "3-5 years", 2, 3))
head(data)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE,include=F}
# This chunk is commented out as we used text format choices in the following study
# # Question: general attitudes
# # variables: "att_purtool", "att_strtool", "att_redtime", "att_evquality", "att_posimpact"
# # 1 - Strongly agree; 2 - Agree; 3 - Neutral; 4 - Disagree; 5 - Strongly disagree; 6 - N/A
# att_mc = c("att_purtool", "att_strtool", "att_redtime", "att_evquality", "att_posimpact")
# 
# invisible(lapply(att_mc, FUN = function(x) {
#   data[[x]] <<- ifelse(data[[x]] == "Strongly agree", 1,
#                      ifelse(data[[x]] == "Agree", 2,
#                             ifelse(data[[x]] == "Neutral", 3,
#                                    ifelse(data[[x]] == "Disagree", 4,
#                                           ifelse(data[[x]] == "Strongly disagree", 5, 6)))))
# }))
# 
# head(data)
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE,include=F}
#split check all that apply responses into indicators
# Question 1: minority leadership
data = mutate(data, di_mled_top = NA, di_mled_board = NA, di_mled_rep = NA, di_mled_na = NA)

invisible(lapply(1:nrow(data), FUN = function(x) {
  choicelist = strsplit(data$di_mled[x], ", ")[[1]]
  if ("Our top executive position is held by a minority." %in% choicelist) {
    data$di_mled_top[x] <<- 1
  } else { 
    data$di_mled_top[x] <<- 0
  }
  
  if ("More than 50% of our board is made up of minorities." %in% choicelist) {
    data$di_mled_board[x] <<- 1
  } else { 
    data$di_mled_board[x] <<- 0
  }
  
  if ("More than 50% of program recipients are minorities." %in% choicelist) {
    data$di_mled_rep[x] <<- 1
  } else { 
    data$di_mled_rep[x] <<- 0
  }
  
  if ("None of the above" %in% choicelist) {
    data$di_mled_na[x] <<- 1
  } else { 
    data$di_mled_na[x] <<- 0
  }
}))

head(data)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE,include=F}
# Question 2: With the money you have saved on purchasing, storing, and maintaining tools and equipment through the TB, what have you been able to accomplish?
data = mutate(data, ci_exaccomp_stf = NA, ci_exaccomp_prj = NA, ci_exaccomp_na = NA, ci_exaccomp_otr = NA)

invisible(lapply(1:nrow(data), FUN = function(x) {
  choicelist = strsplit(data$ci_exaccomp[x], ", ")[[1]]
  if ("Hired additional staff positions" %in% choicelist) {
    data$ci_exaccomp_stf[x] <<- 1
  } else { 
    data$ci_exaccomp_stf[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Hired additional staff positions"]
  
  if ("Hosted additional projects or events" %in% choicelist) {
    data$ci_exaccomp_prj[x] <<- 1
  } else { 
    data$ci_exaccomp_prj[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Hosted additional projects or events"]
  
  
  if ("N/A" %in% choicelist) {
    data$ci_exaccomp_na[x] <<- 1
  } else { 
    data$ci_exaccomp_na[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "N/A"]
  
  if (length(choicelist > 0)) {
    print(x)
    data$ci_exaccomp_otr[x] <<- paste(choicelist, collapse = ", ")
  }
}))

head(data)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include = F}
# Question 3: Without the TB, what would you no longer be able to fund?
data = mutate(data, ci_cutfund_stf = NA, ci_cutfund_prj = NA, ci_cutfund_na = NA, ci_cutfund_otr = NA)

invisible(lapply(1:nrow(data), FUN = function(x) {
  choicelist = strsplit(data$ci_cutfund[x], ", ")[[1]]
  if ("Staff" %in% choicelist) {
    data$ci_cutfund_stf[x] <<- 1
  } else { 
    data$ci_cutfund_stf[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Staff"]
  
  if ("Projects" %in% choicelist) {
    data$ci_cutfund_prj[x] <<- 1
  } else { 
    data$ci_cutfund_prj[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Projects"]
  
  
  if ("N/A" %in% choicelist) {
    data$ci_cutfund_na[x] <<- 1
  } else { 
    data$ci_cutfund_na[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "N/A"]
  
  if (length(choicelist > 0)) {
    print(x)
    data$ci_cutfund_otr[x] <<- paste(choicelist, collapse = ", ")
  }
}))

head(data)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include = F}
# Question 4: Without the TB, which of the following are ways that your community events would be impacted? (check all that apply)
data = mutate(data, ci_evimpact_qtt = NA, ci_evimpact_qlt = NA, ci_evimpact_dvt = NA, 
              ci_evimpact_cst = NA, ci_evimpact_otr = NA)

invisible(lapply(1:nrow(data), FUN = function(x) {
  choicelist = strsplit(data$ci_evimpact[x], ", ")[[1]]
  if ("Quantity" %in% choicelist) {
    data$ci_evimpact_qtt[x] <<- 1
  } else { 
    data$ci_evimpact_qtt[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Quantity"]
  
  if ("Quality" %in% choicelist) {
    data$ci_evimpact_qlt[x] <<- 1
  } else { 
    data$ci_evimpact_qlt[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Quality"]
  
  
  if ("Diversity" %in% choicelist) {
    data$ci_evimpact_dvt[x] <<- 1
  } else { 
    data$ci_evimpact_dvt[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Diversity"]
  
  if ("Consistency" %in% choicelist) {
    data$ci_evimpact_cst[x] <<- 1
  } else { 
    data$ci_evimpact_cst[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Consistency"]
  
  if (length(choicelist > 0)) {
    print(x)
    data$ci_evimpact_otr[x] <<- paste(choicelist, collapse = ", ")
  }
}))

head(data)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
# Question 5: Which of the following types of events have TB tools and equipment helped your CBO complete?
data = mutate(data, eve_type_fr = NA, eve_type_sp = NA, eve_type_ew = NA, eve_type_cb = NA, eve_type_otr = NA)

invisible(lapply(1:nrow(data), FUN = function(x) {
  choicelist = strsplit(data$eve_type[x], ", ")[[1]]
  if ("Fundraising" %in% choicelist) {
    data$eve_type_fr[x] <<- 1
  } else { 
    data$eve_type_fr[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Fundraising"]
  
  if ("Service Projects" %in% choicelist) {
    data$eve_type_sp[x] <<- 1
  } else { 
    data$eve_type_sp[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Service Projects"]
  
  
  if ("Educational Workshops" %in% choicelist) {
    data$eve_type_ew[x] <<- 1
  } else { 
    data$eve_type_ew[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Educational Workshops"]
  
  if ("Community Building" %in% choicelist) {
    data$eve_type_cb[x] <<- 1
  } else { 
    data$eve_type_cb[x] <<- 0
  }
  
  choicelist = choicelist[choicelist != "Community Building"]
  
  if (length(choicelist > 0)) {
    print(x)
    data$eve_type_otr[x] <<- paste(choicelist, collapse = ", ")
  }
}))

head(data)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#5. Merge Gross Recipts to datasheet and add stratification
data$cbo_gr = NA

for (org in unique(data$di_org)) {
  if(is.numeric(data_gr[data_gr$cbo_name == org,]$cbo_gr[1][[1]])) {
    data[data$di_org == org, ]$cbo_gr = data_gr[data_gr$cbo_name == org,]$cbo_gr[1][[1]]
  }
}

# stratification: small < 500,000; median 500,000 - 1,000,000; large >= 1,000,000
# data$cbo_size = ifelse(is.na(data$cbo_gr), NA, 
#                        ifelse(data$cbo_gr < 500000, 1,
#                               ifelse(data$cbo_gr < 1000000, 2, 3)))
# 
# data$cbo_size_str = ifelse(is.na(data$cbo_gr), NA, 
#                        ifelse(data$cbo_gr < 500000, "500,000 or less",
#                               ifelse(data$cbo_gr < 1000000, "b/w 500,000 and 1,000,000", 
#                                      "over 1,000,000")))

# stratification based on Noah's guess: small < 500,000; median 500,000 - 1,000,000; large >= 1,000,000

data$cbo_size = ifelse(data_gr$cbo_size == "Small", 1,
                       ifelse(data_gr$cbo_size == "Medium", 2, 3))

data$cbo_size_str = ifelse(data_gr$cbo_size == "Small", "500,000 or less",
                       ifelse(data_gr$cbo_size == "Medium", "b/w 500,000 and 1,000,000", "over 1,000,000"))

head(data)
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
## Demographic Information 
### Question: How long have you worked with this organization? 
# list the data as a table as the data is binned instead of continuous
table(data$di_orgyearsworked) 
di_orgyearsworked_table = data.frame(cbind(time = c("0-2 years", "3-5 years", "More than 5 years"),
                                RespondentCount = table(data$di_orgyearsworked),
                                Percentage = round(table(data$di_orgyearsworked)/nrow(data),3)))

di_orgyearsworked_table
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
# mean number of year worked with the organization. Transfer choices into number by the following standard: 0-2 years -> 1yr; 3-5 years -> 4 yr; more than 5 years -> 6 year
data = mutate(data, di_orgyearsworked_calc = ifelse(di_orgyearsworked == 1, 1, 
                                                    ifelse(di_orgyearsworked == 2, 4, 6)))
mean(data$di_orgyearsworked_calc)
sd(data$di_orgyearsworked_calc)
median(data$di_orgyearsworked_calc)
hist(data$di_orgyearsworked_calc, breaks = c(0, 3, 6, 9), right = F, xlim = c(0, 10), ylim = c(0, 25), main = "Time Respondents Have Worked with Their Organizations", xlab = "time (years)")
```



```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
### Question 3: The following question pertains to minority leadership and service. For the purpose of this question, minority is defined as women, people of color, and immigrants. Ehich of the following best describes your organization? (please provide your best estimate).?
#Percent of respondents stating, "our top executive position is held by a minority"

table_di_mled_top <- table(data$di_mled_top)
percentages <- prop.table(table_di_mled_top)
#extract percentages for table further down
pct_top_yes <- round(prop.table(table_di_mled_top)[[2]]*100)
pct_top_no <- round(prop.table(table_di_mled_top)[[1]]*100)
count_top_yes <- table_di_mled_top[[2]]
count_top_no <- table_di_mled_top[[1]]

summary_tabledi_mled_top <-data.frame(count=table_di_mled_top, Percentage=percentages)
print(summary_tabledi_mled_top)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#Percent of respondents stating, "More than 50% of our board is made up of minorities "
table_di_mled_board<- table(data$di_mled_board)
percentages <- prop.table(table_di_mled_board)
#extract percentages for table further down
pct_board_yes <- round(prop.table(table_di_mled_board)[[2]]*100)
pct_board_no <- round(prop.table(table_di_mled_board)[[1]]*100)
count_board_yes <- table_di_mled_board[[2]]
count_board_no <- table_di_mled_board[[1]]
summary_tabledi_mled_board <-data.frame(count=table_di_mled_board, Percentage=percentages)
print(summary_tabledi_mled_board)
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#Percent of respondents stating, "More than 50% of program recipients are minorities"
table_di_mled_rep<- table(data$di_mled_rep)
percentages <- prop.table(table_di_mled_rep)
#extract percentages for table further down
pct_recip_yes <- round(prop.table(table_di_mled_rep)[[2]]*100)
pct_recip_no <- round(prop.table(table_di_mled_rep)[[1]]*100)
count_recip_yes <- table_di_mled_rep[[2]]
count_recip_no <- table_di_mled_rep[[1]]

summary_tabledi_mled_rep <-data.frame(count=table_di_mled_rep, Percentage=percentages)
print(summary_tabledi_mled_rep)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#Percent of respondents stating, "None of the above"
table_di_mled_na<- table(data$di_mled_na)
percentages <- prop.table(table_di_mled_na)
#extract percentages for table further down
pct_none_yes <- round(prop.table(table_di_mled_na)[[2]]*100)
pct_none_no <- round(prop.table(table_di_mled_na)[[1]]*100)
count_none_yes <- table_di_mled_na[[2]]
count_none_no <- table_di_mled_na[[1]]

summary_tabledi_mled_na <-data.frame(count=table_di_mled_na, Percentage=percentages)
print(summary_tabledi_mled_na)
```


# Section 2: Community Based Organization Attitudes Towards ToolBank Impact
Respondents were asked five questions to assess their attitudes towards the ToolBank's impact on their organization and their community. Respondents were asked to rank their agreement with statements on a scale from strongly agree to strongly disagree, including options for neutral and not applicable. The statements included the following: 

- "The ToolBank (TB) has positively impacted our Community-Based Organization (CBO) by reducing costs related to purchasing or renting tools and equipment"; 
- "The TB has positively impacted our CBO by reducing costs related to storing tools and equipment";
- "The TB has positively impacted our CBO by reducing staff time to complete community projects";
- "Tools made available through the TB allow our CBO to complete higher quality events/projects without additional funding";
-"The TB has positively impacted our CBO"


**Figure 1: Respondent Attitudes Toward ToolBank Impact**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#overall 
data%>%
  mutate(num_orgs = n())%>%
  pivot_longer(cols=att_purtool:att_posimpact,names_to="question",values_to="response")%>%
  group_by(question)%>%
  summarize(agree = sum(response=="Agree",na.rm=T)/n(),
            strongly_agree = sum(response=="Strongly agree",na.rm=T)/n(),
            neutral = sum(response=="Neutral",na.rm=T)/n(),
            disagree = sum(response=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(response=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(response=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=question)) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="General Attitude", 
       y="Percentage of respondants",
       title="Respondent Attitudes Toward ToolBank Impact") +
  scale_x_discrete(labels = c("higher quality event", "positive impact", "purchase tool", "reduce time", "store tool")) +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#creating a table to give these summary stats
#n respondants 
num_resp <- nrow(data)

#att_purtool: the ToolBank (TB) has positively impacted our CBO by reducing costs related to purchasing or renting tools and equipment
table_att_purtool<- as.data.frame(table(data$att_purtool))
list_of_names <- unique(as.character(table_att_purtool$Var1))
list_of_counts <- c(as.character(table_att_purtool$Freq))


count_purtool_s_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly disagree"))]
count_purtool_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Disagree"))]
count_purtool_n_initial <- list_of_counts[as.numeric(which(list_of_names=="Neutral"))]
count_purtool_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Agree"))]
count_purtool_s_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly agree"))]
count_purtool_na_initial <- list_of_counts[as.numeric(which(list_of_names=="N/A"))]

#strongly disagree
if(is_empty(count_purtool_s_d_initial)){
    count_purtool_s_d <- 0
    pct_purtool_s_d <- 0
}else{
    count_purtool_s_d <- as.numeric(count_purtool_s_d_initial)
    pct_purtool_s_d <- round(count_purtool_s_d/num_resp*100,1)
}
#disagree
if(is_empty(count_purtool_d_initial)){
    count_purtool_d <- 0
    pct_purtool_d <- 0
}else{
    count_purtool_d <-  as.numeric(count_purtool_d_initial)
    pct_purtool_d <- round(count_purtool_d/num_resp*100,1)
}
#neutral
if(is_empty(count_purtool_n_initial)){
    count_purtool_n <- 0
    pct_purtool_n <- 0
}else{
    count_purtool_n <-  as.numeric(count_purtool_n_initial)
    pct_purtool_n <- round(count_purtool_n/num_resp*100,1)
}
#agree
if(is_empty(count_purtool_a_initial)){
    count_purtool_a <- 0
    pct_purtool_a <- 0
}else{
    count_purtool_a <-  as.numeric(count_purtool_a_initial)
    pct_purtool_a <- round(count_purtool_a/num_resp*100,1)
}
#stronngly agree
if(is_empty(count_purtool_s_a_initial)){
    count_purtool_s_a <- 0
    pct_purtool_s_a <- 0
}else{
    count_purtool_s_a <-  as.numeric(count_purtool_s_a_initial)
    pct_purtool_s_a <- round(count_purtool_s_a/num_resp*100,1)
}
#na
if(is_empty(count_purtool_na_initial)){
    count_purtool_na <- 0
    pct_purtool_na <- 0
}else{
    count_purtool_na <- as.numeric(count_purtool_na_initial)
    pct_purtool_na <- round(count_purtool_na/num_resp*100,1)
}




#att_strtool: the TB has positively impacted our CBO by reducing costs related to storing tools and equipment
table_att_strtool<- as.data.frame(table(data$att_strtool))
list_of_names <- unique(as.character(table_att_strtool$Var1))
list_of_counts <- c(as.character(table_att_strtool$Freq))


count_strtool_s_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly disagree"))]
count_strtool_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Disagree"))]
count_strtool_n_initial <- list_of_counts[as.numeric(which(list_of_names=="Neutral"))]
count_strtool_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Agree"))]
count_strtool_s_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly agree"))]
count_strtool_na_initial <- list_of_counts[as.numeric(which(list_of_names=="N/A"))]

#strongly disagree
if(is_empty(count_strtool_s_d_initial)){
    count_strtool_s_d <- 0
    pct_strtool_s_d <- 0
}else{
    count_strtool_s_d <- as.numeric(count_strtool_s_d_initial)
    pct_strtool_s_d <- round(count_strtool_s_d/num_resp*100,1)
}
#disagree
if(is_empty(count_strtool_d_initial)){
    count_strtool_d <- 0
    pct_strtool_d <- 0
}else{
    count_strtool_d <-  as.numeric(count_strtool_d_initial)
    pct_strtool_d <- round(count_strtool_d/num_resp*100,1)
}
#neutral
if(is_empty(count_strtool_n_initial)){
    count_strtool_n <- 0
    pct_strtool_n <- 0
}else{
    count_strtool_n <-  as.numeric(count_strtool_n_initial)
    pct_strtool_n <- round(count_strtool_n/num_resp*100,1)
}
#agree
if(is_empty(count_strtool_a_initial)){
    count_strtool_a <- 0
    pct_strtool_a <- 0
}else{
    count_strtool_a <-  as.numeric(count_strtool_a_initial)
    pct_strtool_a <- round(count_strtool_a/num_resp*100,1)
}
#stronngly agree
if(is_empty(count_strtool_s_a_initial)){
    count_strtool_s_a <- 0
    pct_strtool_s_a <- 0
}else{
    count_strtool_s_a <-  as.numeric(count_strtool_s_a_initial)
    pct_strtool_s_a <- round(count_strtool_s_a/num_resp*100,1)
}
#na
if(is_empty(count_strtool_na_initial)){
    count_strtool_na <- 0
    pct_strtool_na <- 0
}else{
    count_strtool_na <- as.numeric(count_strtool_na_initial)
    pct_strtool_na <- round(count_strtool_na/num_resp*100,1)
}

#att_redtime: theTB has positively impacted our CBO by reducing staff time to complete maintenance/projects
table_att_redtime<- as.data.frame(table(data$att_redtime))
list_of_names <- unique(as.character(table_att_redtime$Var1))
list_of_counts <- c(as.character(table_att_redtime$Freq))


count_redtime_s_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly disagree"))]
count_redtime_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Disagree"))]
count_redtime_n_initial <- list_of_counts[as.numeric(which(list_of_names=="Neutral"))]
count_redtime_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Agree"))]
count_redtime_s_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly agree"))]
count_redtime_na_initial <- list_of_counts[as.numeric(which(list_of_names=="N/A"))]

#strongly disagree
if(is_empty(count_redtime_s_d_initial)){
    count_redtime_s_d <- 0
    pct_redtime_s_d <- 0
}else{
    count_redtime_s_d <- as.numeric(count_redtime_s_d_initial)
    pct_redtime_s_d <- round(count_redtime_s_d/num_resp*100,1)
}
#disagree
if(is_empty(count_redtime_d_initial)){
    count_redtime_d <- 0
    pct_redtime_d <- 0
}else{
    count_redtime_d <-  as.numeric(count_redtime_d_initial)
    pct_redtime_d <- round(count_redtime_d/num_resp*100,1)
}
#neutral
if(is_empty(count_redtime_n_initial)){
    count_redtime_n <- 0
    pct_redtime_n <- 0
}else{
    count_redtime_n <-  as.numeric(count_redtime_n_initial)
    pct_redtime_n <- round(count_redtime_n/num_resp*100,1)
}
#agree
if(is_empty(count_redtime_a_initial)){
    count_redtime_a <- 0
    pct_redtime_a <- 0
}else{
    count_redtime_a <-  as.numeric(count_redtime_a_initial)
    pct_redtime_a <- round(count_redtime_a/num_resp*100,1)
}
#stronngly agree
if(is_empty(count_redtime_s_a_initial)){
    count_redtime_s_a <- 0
    pct_redtime_s_a <- 0
}else{
    count_redtime_s_a <-  as.numeric(count_redtime_s_a_initial)
    pct_redtime_s_a <- round(count_redtime_s_a/num_resp*100,1)
}
#na
if(is_empty(count_redtime_na_initial)){
    count_redtime_na <- 0
    pct_redtime_na <- 0
}else{
    count_redtime_na <- as.numeric(count_redtime_na_initial)
    pct_redtime_na <- round(count_redtime_na/num_resp*100,1)
}


#att_evquality:  "the Tools made available through the TB allow our CBO to complete higher quality events/projects without additional funding
table_att_evquality<- as.data.frame(table(data$att_evquality))
list_of_names <- unique(as.character(table_att_evquality$Var1))
list_of_counts <- c(as.character(table_att_evquality$Freq))


count_evquality_s_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly disagree"))]
count_evquality_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Disagree"))]
count_evquality_n_initial <- list_of_counts[as.numeric(which(list_of_names=="Neutral"))]
count_evquality_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Agree"))]
count_evquality_s_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly agree"))]
count_evquality_na_initial <- list_of_counts[as.numeric(which(list_of_names=="N/A"))]

#strongly disagree
if(is_empty(count_evquality_s_d_initial)){
    count_evquality_s_d <- 0
    pct_evquality_s_d <- 0
}else{
    count_evquality_s_d <- as.numeric(count_evquality_s_d_initial)
    pct_evquality_s_d <- round(count_evquality_s_d/num_resp*100,1)
}
#disagree
if(is_empty(count_evquality_d_initial)){
    count_evquality_d <- 0
    pct_evquality_d <- 0
}else{
    count_evquality_d <-  as.numeric(count_evquality_d_initial)
    pct_evquality_d <- round(count_evquality_d/num_resp*100,1)
}
#neutral
if(is_empty(count_evquality_n_initial)){
    count_evquality_n <- 0
    pct_evquality_n <- 0
}else{
    count_evquality_n <-  as.numeric(count_evquality_n_initial)
    pct_evquality_n <- round(count_evquality_n/num_resp*100,1)
}
#agree
if(is_empty(count_evquality_a_initial)){
    count_evquality_a <- 0
    pct_evquality_a <- 0
}else{
    count_evquality_a <-  as.numeric(count_evquality_a_initial)
    pct_evquality_a <- round(count_evquality_a/num_resp*100,1)
}
#stronngly agree
if(is_empty(count_evquality_s_a_initial)){
    count_evquality_s_a <- 0
    pct_evquality_s_a <- 0
}else{
    count_evquality_s_a <-  as.numeric(count_evquality_s_a_initial)
    pct_evquality_s_a <- round(count_evquality_s_a/num_resp*100,1)
}
#na
if(is_empty(count_evquality_na_initial)){
    count_evquality_na <- 0
    pct_evquality_na <- 0
}else{
    count_evquality_na <- as.numeric(count_evquality_na_initial)
    pct_evquality_na <- round(count_evquality_na/num_resp*100,1)
}

#att_posimpact:  TB has positively impacted our CBO 
table_att_posimpact<- as.data.frame(table(data$att_posimpact))
list_of_names <- unique(as.character(table_att_posimpact$Var1))
list_of_counts <- c(as.character(table_att_posimpact$Freq))


count_posimpact_s_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly disagree"))]
count_posimpact_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Disagree"))]
count_posimpact_n_initial <- list_of_counts[as.numeric(which(list_of_names=="Neutral"))]
count_posimpact_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Agree"))]
count_posimpact_s_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly agree"))]
count_posimpact_na_initial <- list_of_counts[as.numeric(which(list_of_names=="N/A"))]

#strongly disagree
if(is_empty(count_posimpact_s_d_initial)){
    count_posimpact_s_d <- 0
    pct_posimpact_s_d <- 0
}else{
    count_posimpact_s_d <- as.numeric(count_posimpact_s_d_initial)
    pct_posimpact_s_d <- round(count_posimpact_s_d/num_resp*100,1)
}
#disagree
if(is_empty(count_posimpact_d_initial)){
    count_posimpact_d <- 0
    pct_posimpact_d <- 0
}else{
    count_posimpact_d <-  as.numeric(count_posimpact_d_initial)
    pct_posimpact_d <- round(count_posimpact_d/num_resp*100,1)
}
#neutral
if(is_empty(count_posimpact_n_initial)){
    count_posimpact_n <- 0
    pct_posimpact_n <- 0
}else{
    count_posimpact_n <-  as.numeric(count_posimpact_n_initial)
    pct_posimpact_n <- round(count_posimpact_n/num_resp*100,1)
}
#agree
if(is_empty(count_posimpact_a_initial)){
    count_posimpact_a <- 0
    pct_posimpact_a <- 0
}else{
    count_posimpact_a <-  as.numeric(count_posimpact_a_initial)
    pct_posimpact_a <- round(count_posimpact_a/num_resp*100,1)
}
#stronngly agree
if(is_empty(count_posimpact_s_a_initial)){
    count_posimpact_s_a <- 0
    pct_posimpact_s_a <- 0
}else{
    count_posimpact_s_a <-  as.numeric(count_posimpact_s_a_initial)
    pct_posimpact_s_a <- round(count_posimpact_s_a/num_resp*100,1)
}
#na
if(is_empty(count_posimpact_na_initial)){
    count_posimpact_na <- 0
    pct_posimpact_na <- 0
}else{
    count_posimpact_na <- as.numeric(count_posimpact_na_initial)
    pct_posimpact_na <- round(count_posimpact_na/num_resp*100,1)
}

```



```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}

#table summarizing demographic info
output_continuous <- matrix(c(
  
# att_purtool:"TB has pos. impacted our CBO by reducing costs related to purchasing or renting tools and equipment",
  # "# Strongly Agree (%)", 
  paste0(count_purtool_s_a," (",pct_purtool_s_a,"%)"),
  # "# Agree (%)",
  paste0(count_purtool_a," (",pct_purtool_a,"%)"),
  # "# Neutral (%)",
  paste0(count_purtool_n," (",pct_purtool_n,"%)"),
  # "# Disagree (%)",
  paste0(count_purtool_d," (",pct_purtool_d,"%)"),
  # "# Strongly Disagree (%)",
  paste0(count_purtool_s_d," (",pct_purtool_s_d,"%)"),
  # "# N/A (%)"
  paste0(count_purtool_na," (",pct_purtool_na,"%)"),
  
# att_strtool:"TB has pos. impacted our CBO by reducing costs related to storing tools and equipment",
  # "# Strongly Agree (%)", 
  paste0(count_strtool_s_a," (",pct_strtool_s_a,"%)"),
  # "# Agree (%)",
  paste0(count_strtool_a," (",pct_strtool_a,"%)"),
  # "# Neutral (%)",
  paste0(count_strtool_n," (",pct_strtool_n,"%)"),
  # "# Disagree (%)",
  paste0(count_strtool_d," (",pct_strtool_d,"%)"),
  # "# Strongly Disagree (%)",
  paste0(count_strtool_s_d," (",pct_strtool_s_d,"%)"),
  # "# N/A (%)"
  paste0(count_strtool_na," (",pct_strtool_na,"%)"),

# att_redtime:"TB has pos. impacted our CBO by reducing staff time to complete maintenance/projects",
  # "# Strongly Agree (%)", 
  paste0(count_redtime_s_a," (",pct_redtime_s_a,"%)"),
  # "# Agree (%)",
  paste0(count_redtime_a," (",pct_redtime_a,"%)"),
  # "# Neutral (%)",
  paste0(count_redtime_n," (",pct_redtime_n,"%)"),
  # "# Disagree (%)",
  paste0(count_redtime_d," (",pct_redtime_d,"%)"),
  # "# Strongly Disagree (%)",
  paste0(count_redtime_s_d," (",pct_redtime_s_d,"%)"),
  # "# N/A (%)"
  paste0(count_redtime_na," (",pct_redtime_na,"%)"),
# att_evquality: "the Tools made available through the TB allow our CBO to complete higher quality events/projects without additional funding",
  # "# Strongly Agree (%)", 
  paste0(count_evquality_s_a," (",pct_evquality_s_a,"%)"),
  # "# Agree (%)",
  paste0(count_evquality_a," (",pct_evquality_a,"%)"),
  # "# Neutral (%)",
  paste0(count_evquality_n," (",pct_evquality_n,"%)"),
  # "# Disagree (%)",
  paste0(count_evquality_d," (",pct_evquality_d,"%)"),
  # "# Strongly Disagree (%)",
  paste0(count_evquality_s_d," (",pct_evquality_s_d,"%)"),
  # "# N/A (%)"
  paste0(count_evquality_na," (",pct_evquality_na,"%)"),

# att_posimpact: "TB has pos. impacted our CBO"
  # "# Strongly Agree (%)", 
  paste0(count_posimpact_s_a," (",pct_posimpact_s_a,"%)"),
  # "# Agree (%)",
  paste0(count_posimpact_a," (",pct_posimpact_a,"%)"),
  # "# Neutral (%)",
  paste0(count_posimpact_n," (",pct_posimpact_n,"%)"),
  # "# Disagree (%)",
  paste0(count_posimpact_d," (",pct_posimpact_d,"%)"),
  # "# Strongly Disagree (%)",
  paste0(count_posimpact_s_d," (",pct_posimpact_s_d,"%)"),
  # "# N/A (%)"
  paste0(count_posimpact_na," (",pct_posimpact_na,"%)")


),

         ncol = 6, byrow = TRUE)

output_continuous%>% 
  addHtmlTableStyle(col.columns = c("none", "#F7F7F7"),
                    col.rgroup = c("none", "#F5FBFF")
                    )%>% 
  htmlTable(header =  c("#Strongly Agree (%)", 
                        "#Agree (%)",
                        "#Neutral (%)",
                        "#Disagree (%)",
                        "#Strongly Disagree (%)",
                        "#N/A (%)"),
            rnames = c(
"TB has pos. impacted our CBO by reducing costs related to purchasing or renting tools and equipment",
"TB has pos. impacted our CBO by reducing costs related to storing tools and equipment",
"TB has pos. impacted our CBO by reducing staff time to complete maintenance/projects",
"the Tools made available through the TB allow our CBO to complete higher quality events/projects without additional funding",
"TB has pos. impacted our CBO"

            ),
            # rgroup = c("Sentiment "),
            # n.rgroup = c(4),
            caption = "Number, percentages of respondents to sentiment questions"
            )

```
**Findings**

- 100% of respondents strongly agreed (93.3%) or agreed (6.7%) that the ToolBank positively impacts their CBO 
- 100% of respondents strongly agreed (93.3%) or agreed (6.7%) that the ToolBank reduced costs related to purchasing and renting tools and equipment
- More than 95% or respondents strongly agreed (80.0%) or agreed (15.6%) that the tools made available through the ToolBank allow their CBO to complete higher quality events/projects without additional funding
- Respondents have comparatively less positive attitudes towards (still more than 60% of the respondent strongly agreed or agreed) the statements that the ToolBank positively impacted their CBO by reducing costs related to storing tools and equipment, and the ToolBank has positively impacted their CBO by reducing staff time to complete maintenance/project



# Section 3: General Attitudes Stratified by Respondent and Community Based Organization (CBO) Characteristics 
The following plots analyze the questions from section one above, stratified by the number of years that the respondent reported working at the CBO, the size of the CBO, and the minority status of the CBO. These plots explore if there is a relationship between these self-reported characteristics and the respondents' attitudes towards the ToolBank's economic and community impact.  

### General Attitudes Stratified by Respondent Years with the CBO
The following plots analyze the questions from section two, stratified by the number of years that the respondent reported working at the CBO. These plots explore if there is a relationship between respondents' self-reported number of years with the CBO and their attitudes towards the ToolBank's economic and community impact.

**Figure 2: Respondent Agreement that the ToolBank Reduced Their CBOs Costs Related to Purchasing and Renting Tools and Equipment, Stratified by Respondent Years with the CBO**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#The ToolBank (TB) has positively impacted our CBO by reducing costs related to purchasing or renting tools and equipment
data%>%
  group_by(di_orgyearsworked)%>%
  summarize(agree = sum(att_purtool=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_purtool=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_purtool=="Neutral",na.rm=T)/n(),
            disagree = sum(att_purtool=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_purtool=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_purtool=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(di_orgyearsworked))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Years Worked at CBO", 
       y="Percentage of respondents",
       title="Respondent Agreement that TB Reduced Purchasing and Renting Costs") +
  scale_x_discrete(labels = c("0-2 years", "3-5 years", "More than 5 years")) +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))

```

**Figure 3: Respondent Agreement that the ToolBank Reduced Their CBOs Costs Related Storing Tools and Equipment, Stratified by Respondent Years with the CBO**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#The TB has positively impacted our CBO by reducing costs related to storing tools and equipment
data%>%
  group_by(di_orgyearsworked)%>%
  summarize(agree = sum(att_strtool=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_strtool=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_strtool=="Neutral",na.rm=T)/n(),
            disagree = sum(att_strtool=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_strtool=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_strtool=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(di_orgyearsworked))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Years Worked at CBO", 
       y="Percentage of respondants",
       title="Agreement that TB Reduced Costs Related to Storing Tools/equipment") +
  scale_x_discrete(labels = c("0-2 years", "3-5 years", "More than 5 years")) +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))
```


**Figure 4: Respondent Agreement that the ToolBank Reduced Their CBOs Costs Related to Staff Time to Complete Community Projects, Stratified by Respondent Years with the CBO**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#The TB has positively impacted our CBO by reducing staff time to complete community projects
data%>%
  group_by(di_orgyearsworked)%>%
  summarize(agree = sum(att_redtime=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_redtime=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_redtime=="Neutral",na.rm=T)/n(),
            disagree = sum(att_redtime=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_redtime=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_redtime=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(di_orgyearsworked))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Years Worked at CBO", 
       y="Percentage of respondents",
       title="Agreement that TB Reduced Staff Time for Projects") +
  scale_x_discrete(labels = c("0-2 years", "3-5 years", "More than 5 years")) +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))


```



**Figure 5: Respondent Agreement that the ToolBank Has Positively Impacted Their CBO, Stratified by Respondent Years with the CBO**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#The TB has positively impacted our CBO
data%>%
  group_by(di_orgyearsworked)%>%
  summarize(agree = sum(att_posimpact=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_posimpact=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_posimpact=="Neutral",na.rm=T)/n(),
            disagree = sum(att_posimpact=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_posimpact=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_posimpact=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(di_orgyearsworked))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Years Worked at CBO", 
       y="Percentage of respondants",
       title="Respondent Agreement that the ToolBank Has Positively Impacted Their CBO") +
  scale_x_discrete(labels = c("0-2 years", "3-5 years", "More than 5 years")) +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))
```




```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#The ToolBank (TB) has positively impacted our CBO by reducing costs related to purchasing or renting tools and equipment
data%>%
  group_by(di_orgyearsworked)%>%
  summarize(agree = sum(att_purtool=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_purtool=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_purtool=="Neutral",na.rm=T)/n(),
            disagree = sum(att_purtool=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_purtool=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_purtool=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(di_orgyearsworked))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Years Worked at CBO", 
       y="Percentage of respondants",
       title="Agreement that TB Reduced Costs Related to Purchasing/renting Tools/equipment") +
  scale_x_discrete(labels = c("0-2 years", "3-5 years", "More than 5 years"))

#The TB has positively impacted our CBO by reducing costs related to storing tools and equipment
data%>%
  group_by(di_orgyearsworked)%>%
  summarize(agree = sum(att_strtool=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_strtool=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_strtool=="Neutral",na.rm=T)/n(),
            disagree = sum(att_strtool=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_strtool=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_strtool=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(di_orgyearsworked))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Years Worked at CBO", 
       y="Percentage of respondants",
       title="Agreement that TB Reduced Costs Related to Storing Tools/equipment") +
  scale_x_discrete(labels = c("0-2 years", "3-5 years", "More than 5 years"))


#The TB has positively impacted our CBO by reducing staff time to complete community projects
data%>%
  group_by(di_orgyearsworked)%>%
  summarize(agree = sum(att_redtime=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_redtime=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_redtime=="Neutral",na.rm=T)/n(),
            disagree = sum(att_redtime=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_redtime=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_redtime=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(di_orgyearsworked))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Years Worked at CBO", 
       y="Percentage of respondants",
       title="Agreement that TB Reduced Staff Time for Projects") +
  scale_x_discrete(labels = c("0-2 years", "3-5 years", "More than 5 years"))

#Tools made available through the TB allow our CBO to complete higher quality events/projects without additional funding
data%>%
  group_by(di_orgyearsworked)%>%
  summarize(agree = sum(att_evquality=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_evquality=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_evquality=="Neutral",na.rm=T)/n(),
            disagree = sum(att_evquality=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_evquality=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_evquality=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(di_orgyearsworked))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Years Worked at CBO", 
       y="Percentage of respondants",
       title="Agreement that TB Allows for Higher Quality Events/projs") +
  scale_x_discrete(labels = c("0-2 years", "3-5 years", "More than 5 years"))

#The TB has positively impacted our CBO
data%>%
  group_by(di_orgyearsworked)%>%
  summarize(agree = sum(att_posimpact=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_posimpact=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_posimpact=="Neutral",na.rm=T)/n(),
            disagree = sum(att_posimpact=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_posimpact=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_posimpact=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(di_orgyearsworked))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Years Worked at CBO", 
       y="Percentage of respondants",
       title="Agreement that TB Positively Impacted CBO") +
  scale_x_discrete(labels = c("0-2 years", "3-5 years", "More than 5 years")) 
```

**Findings**

- Respondents working with their organization for 3-5 years have slightly more positive opinion towards the TB, however this difference compared to other groups was not statistically significant


### General Attitudes Stratified by Size of CBO
The following plots analyze the general attitude questions from section two, stratified by the size of the organization, as determined by their publicly available gross receipts. These plots explore if there is a relationship between the size of the funding available to the CBO and the respondents' attitudes towards the ToolBank's economic and community impact.

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
### now combine mid-sized, large CBOs
data<- data%>%
  mutate(cbo_size_2_cat = case_when(cbo_size_str =="500,000 or less"~"500,000 or less",
                                    cbo_size_str =="over 1,000,000"~"over 500,000",
                                    cbo_size_str =="b/w 500,000 and 1,000,000"~"over 500,000"))

#extract info from three size categories
table_size<- table(data$cbo_size)
count_size_1 <- table_size[[1]]
count_size_2 <- table_size[[2]]
count_size_3 <- table_size[[3]]
count_size_NA <- sum(is.na(data$cbo_size))
num_obsv <- sum(count_size_1,
                count_size_2,
                count_size_3,
                count_size_NA)
pct_size_1 <- round(count_size_1/num_obsv*100,1)
pct_size_2 <- round(count_size_2/num_obsv*100,1)
pct_size_3 <- round(count_size_3/num_obsv*100,1)
pct_size_NA <- round(count_size_NA/num_obsv*100,1)

#extract info from 2 size categories
table_size_2 <- table(data$cbo_size_2_cat)
count_size_sm <- table_size_2[[1]]
count_size_big <- table_size_2[[2]]

num_obsv <- sum(count_size_sm,
                count_size_big)
pct_size_sm <- round(count_size_sm/num_obsv*100,1)
pct_size_big <- round(count_size_big/num_obsv*100,1)



#table summarizing info, 3 size cats
output_continuous <- matrix(c(
# "Less than 500k (group 1)",
  # number
  count_size_1,
  # pct
  paste0(pct_size_1,"%"),
# "Between 500k and 1000k (group 2)",
  # number
  count_size_2,
  # pct
  paste0(pct_size_2,"%"),
# "Greater than 1000k (group 3)",
  # number
  count_size_3,
  # pct
  paste0(pct_size_3,"%"),
# "NA"
  # number
  count_size_NA,
  # pct
  paste0(pct_size_NA,"%")

),

         ncol = 2, byrow = TRUE)

library(htmlTable)
output_continuous%>% 
  addHtmlTableStyle(col.columns = c("none", "#F7F7F7"))%>% 
  htmlTable(header =  c("Number Respondents   ", "   Percent of Total Respondents"),
            rnames = c(
"Less than 500k (group 1)",
"Between 500k and 1000k (group 2)",
"Greater than 1000k (group 3)",
"NA"
            ),
            rgroup = c("CBO Size"),
            n.rgroup = c(4),
            caption = "Table 2a: Number and Percentage of CBOs by 3 Size Categories"
            )




output_continuous <- matrix(c(
# "Less than 500k (group 1)",
  # number
  count_size_sm,
  # pct
  paste0(pct_size_sm,"%"),
# "Between 500k and 1000k (group 2)",
  # number
  count_size_big,
  # pct
  paste0(pct_size_big,"%")
),

         ncol = 2, byrow = TRUE)

library(htmlTable)
output_continuous%>% 
  addHtmlTableStyle(col.columns = c("none", "#F7F7F7"))%>% 
  htmlTable(header =  c("Number Respondents   ", "   Percent of Total Respondents"),
            rnames = c(
"Less than 500k",
"Greater than 500k"
            ),
            rgroup = c("CBO Size"),
            n.rgroup = c(2),
            caption = "Table 2b: Number and Percentage of CBOs by 2 Size Categories"
            )
```


**Figure 6: Respondent Agreement that the ToolBank Reduced Their CBO's Purchasing and Renting Costs, Stratified by CBO Size**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#The ToolBank (TB) has positively impacted our CBO by reducing costs related to purchasing or renting tools and equipment
data%>%
  group_by(cbo_size_2_cat)%>%
  summarize(agree = sum(att_purtool=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_purtool=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_purtool=="Neutral",na.rm=T)/n(),
            disagree = sum(att_purtool=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_purtool=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_purtool=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(cbo_size_2_cat))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Size of CBO*", 
       y="Percentage of respondents",
       title="Respondent Agreement that TB Reduced Purchasing and Renting Costs") +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))
```

**Figure 7: Respondent Agreement that the ToolBank Reduced Their CBOs Costs Related Storing Tools and Equipment, Stratified by, Stratified by CBO Size**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#The TB has positively impacted our CBO by reducing costs related to storing tools and equipment
data%>%
  group_by(cbo_size_2_cat)%>%
  summarize(agree = sum(att_strtool=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_strtool=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_strtool=="Neutral",na.rm=T)/n(),
            disagree = sum(att_strtool=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_strtool=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_strtool=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(cbo_size_2_cat))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Size of CBO*", 
       y="Percentage of respondents",
       title="Agreement that TB Reduced Costs Related to Storing Tools/equipment",
       caption = "*Groups 1,2 3 are CBOs with size 500kor less, b/w 500k and 1000k, and over 1000k, respectively")  +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))
```


**Figure 8: Respondent Agreement that the ToolBank Reduced Their CBOs Costs Related to Staff Time to Complete Community Projects, Stratified by CBO Size**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#The TB has positively impacted our CBO by reducing staff time to complete community projects
data%>%
  group_by(cbo_size_2_cat)%>%
  summarize(agree = sum(att_redtime=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_redtime=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_redtime=="Neutral",na.rm=T)/n(),
            disagree = sum(att_redtime=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_redtime=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_redtime=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(cbo_size_2_cat))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Size of CBO*", 
       y="Percentage of respondants",
       title="Agreement That TB Reduced Costs Related to Staff Time for Projects",
       caption = "*Groups 1,2 3 are CBOs with size 500kor less, b/w 500k and 1000k, and over 1000k, respectively")+
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))   
```


**Figure 9: Respondent Agreement that the ToolBank Has Positively Impacted Their CBO, Stratified by CBO Size**


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#The TB has positively impacted our CBO
data%>%
  group_by(cbo_size_2_cat)%>%
  summarize(agree = sum(att_posimpact=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_posimpact=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_posimpact=="Neutral",na.rm=T)/n(),
            disagree = sum(att_posimpact=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_posimpact=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_posimpact=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(cbo_size_2_cat))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Size of CBO*", 
       y="Percentage of respondants",
       title="Agreement that TB Postively Impacted the CBO",
       caption = "*Groups 1,2 3 are CBOs with size 500kor less, b/w 500k and 1000k, and over 1000k, respectively") +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))
```



```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#The ToolBank (TB) has positively impacted our CBO by reducing costs related to purchasing or renting tools and equipment
data%>%
  group_by(cbo_size_2_cat)%>%
  summarize(agree = sum(att_purtool=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_purtool=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_purtool=="Neutral",na.rm=T)/n(),
            disagree = sum(att_purtool=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_purtool=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_purtool=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(cbo_size_2_cat))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Size of CBO*", 
       y="Percentage of respondants",
       title="Agreement that TB Reduced Costs Related to Purchasing/renting Tools/equipment",
       caption = "*Groups 1,2 3 are CBOs with size 500kor less, b/w 500k and 1000k, and over 1000k, respectively") 

#The TB has positively impacted our CBO by reducing costs related to storing tools and equipment
data%>%
  group_by(cbo_size_2_cat)%>%
  summarize(agree = sum(att_strtool=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_strtool=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_strtool=="Neutral",na.rm=T)/n(),
            disagree = sum(att_strtool=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_strtool=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_strtool=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(cbo_size_2_cat))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Size of CBO*", 
       y="Percentage of respondants",
       title="Agreement that TB Reduced Costs Related to Storing Tools/equipment",
       caption = "*Groups 1,2 3 are CBOs with size 500kor less, b/w 500k and 1000k, and over 1000k, respectively") 


#The TB has positively impacted our CBO by reducing staff time to complete community projects
data%>%
  group_by(cbo_size_2_cat)%>%
  summarize(agree = sum(att_redtime=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_redtime=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_redtime=="Neutral",na.rm=T)/n(),
            disagree = sum(att_redtime=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_redtime=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_redtime=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(cbo_size_2_cat))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Size of CBO*", 
       y="Percentage of respondants",
       title="Agreement that TB Reduced Staff Time for Projects",
       caption = "*Groups 1,2 3 are CBOs with size 500kor less, b/w 500k and 1000k, and over 1000k, respectively") 

#Tools made available through the TB allow our CBO to complete higher quality events/projects without additional funding
data%>%
  group_by(cbo_size_2_cat)%>%
  summarize(agree = sum(att_evquality=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_evquality=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_evquality=="Neutral",na.rm=T)/n(),
            disagree = sum(att_evquality=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_evquality=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_evquality=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(cbo_size_2_cat))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Size of CBO*", 
       y="Percentage of respondants",
       title="Agreement that TB Allows for Higher Quality Events/projs",
       caption = "*Groups 1,2 3 are CBOs with size 500kor less, b/w 500k and 1000k, and over 1000k, respectively") 

#The TB has positively impacted our CBO
data%>%
  group_by(cbo_size_2_cat)%>%
  summarize(agree = sum(att_posimpact=="Agree",na.rm=T)/n(),
            strongly_agree = sum(att_posimpact=="Strongly agree",na.rm=T)/n(),
            neutral = sum(att_posimpact=="Neutral",na.rm=T)/n(),
            disagree = sum(att_posimpact=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(att_posimpact=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(att_posimpact=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=as.factor(cbo_size_2_cat))) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="Size of CBO*", 
       y="Percentage of respondants",
       title="Agreement that TB Positively Impacted CBO",
       caption = "*Groups 1,2 3 are CBOs with size 500kor less, b/w 500k and 1000k, and over 1000k, respectively") 
```


**Findings:**

- In general, larger and smaller CBOs show similar trends in agreement with benefits from the Toolbank. However, smaller CBOs tend to report slightly stronger levels of agreement

### General Attitudes Stratified Minority Status
The following plots analyze the general attitude questions from section one, stratified by the minority status of the CBO, as determined by respondent self-report. For this survey, minority was defined as women, people of color, non-gender conforming individuals, LGBTQ+ individuals, and immigrants, and respondents were asked if they met one of more the following criteria: 1) the top executive position is held by a minority, 2) more than 50% of the board is made up of minorities, 3) more than 50% of program recipients are minorities, 4) none of the above. Respondents were able to select more than one of each criteria. The plots below explore if there is a relationship between the  minority criteria of the CBO provided by the respondents and the respondents' attitudes towards the ToolBank's economic and community impact.


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#table summarizing demographic info
output_continuous <- matrix(c(
#"our top executive position is held by a minority",
  #yes
  paste0(count_top_yes, " (",pct_top_yes,"%)"),
  #no
  paste0(count_top_no, " (",pct_top_no,"%)"),
#"More than 50% of our board is made up of minorities",
  #yes
  paste0(count_board_yes, " (",pct_board_yes,"%)"),
  #no
  paste0(count_board_no, " (",pct_board_no,"%)"),
#"More than 50% of program recipients are minorities",
  #yes
  paste0(count_recip_yes, " (",pct_recip_yes,"%)"),
  #no
  paste0(count_recip_no, " (",pct_recip_no,"%)"),
#"None of the above"
  #yes
  paste0(count_none_yes, " (",pct_none_yes,"%)"),
  #no
  paste0(count_none_no, " (",pct_none_no,"%)")
),

         ncol = 2, byrow = TRUE)

output_continuous%>% 
  addHtmlTableStyle(col.columns = c("none", "#F7F7F7"))%>% 
  htmlTable(header =  c("# Yes (% Yes) ", "# No (% No)"),
            rnames = c(
"Our top executive position is held by a minority",
"More than 50% of our board is made up of minorities",
"More than 50% of program recipients are minorities",
"None of the above"
            ),
            rgroup = c("Minority Leadership"),
            n.rgroup = c(4),
            caption = " Table 3: Number, percentages of respondants indicating minority leadership"
            )
```


**Figure 10: General Attitudes Toward ToolBank Impact Among Respondents Reporting a Top Executive with Minority Status **

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#The ToolBank (TB) has positively impacted our CBO by reducing costs related to purchasing or renting tools and equipment
data <- data%>%
  mutate(top_exec_minority = str_detect(di_mled,"Our top executive position is held by a minority."),
         maj_prog_recip_minority = str_detect(di_mled,"More than 50% of program recipients are minorities"),
         none = str_detect(di_mled,"None of the above"),
         maj_board_minority = str_detect(di_mled,"More than 50% of our board is made up of minorities"),
         )

                                                                                                                                    
# sentiments of top exec minority
data%>%
  filter(top_exec_minority==TRUE)%>%
  pivot_longer(cols=att_purtool:att_posimpact,names_to="question",values_to="response")%>%
  group_by(question)%>%
  summarize(agree = sum(response=="Agree",na.rm=T)/n(),
            strongly_agree = sum(response=="Strongly agree",na.rm=T)/n(),
            neutral = sum(response=="Neutral",na.rm=T)/n(),
            disagree = sum(response=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(response=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(response=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=question)) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="General Attitude", 
       y="Percentage of respondents",
       title="Sentiment on TB among CBOs w/ top exec. a minority") +
  scale_x_discrete(labels = c("higher quality event", "positive impact", "purchase tool", "reduce time", "store tool")) +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))
```

**Figure 11: General Attitudes Toward ToolBank Impact Among Respondents Indicating More Than 50% of Program Recipients as Minorities**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
# sentiments of CBOS w "More than 50% of program recipients are minorities"
data%>%
  filter(maj_prog_recip_minority==TRUE)%>%
  pivot_longer(cols=att_purtool:att_posimpact,names_to="question",values_to="response")%>%
  group_by(question)%>%
  summarize(agree = sum(response=="Agree",na.rm=T)/n(),
            strongly_agree = sum(response=="Strongly agree",na.rm=T)/n(),
            neutral = sum(response=="Neutral",na.rm=T)/n(),
            disagree = sum(response=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(response=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(response=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=question)) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="General Attitude", 
       y="Percentage of respondants",
       title="Sentiment on TB among CBOs w/ 50%+ program recipients are minorities") +
  scale_x_discrete(labels = c("higher quality event", "positive impact", "purchase tool", "reduce time", "store tool")) +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))

```

**Figure 12: General Attitudes Toward ToolBank Impact Among Respondents Indicating More Than 50% of CBO Board Members are Minorities**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#sentiment of CBOs w "More than 50% of our board is made up of minorities"
data%>%
  filter(maj_board_minority==TRUE)%>%
  pivot_longer(cols=att_purtool:att_posimpact,names_to="question",values_to="response")%>%
  group_by(question)%>%
  summarize(agree = sum(response=="Agree",na.rm=T)/n(),
            strongly_agree = sum(response=="Strongly agree",na.rm=T)/n(),
            neutral = sum(response=="Neutral",na.rm=T)/n(),
            disagree = sum(response=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(response=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(response=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=question)) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="General Attitude", 
       y="Percentage of respondants",
       title="Sentiment on TB among CBOs w/ 50%+ board members are minorities") +
  scale_x_discrete(labels = c("higher quality event", "positive impact", "purchase tool", "reduce time", "store tool")) +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))

```



**Figure 13: General Attitudes Toward ToolBank Impact Among Respondents Indicating Their CBO Did Not Meet Any of the Minority Status Criteria Provided**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
# sentiments of CBOs who responded "None of the above"
data%>%
  filter(none==TRUE)%>%
  pivot_longer(cols=att_purtool:att_posimpact,names_to="question",values_to="response")%>%
  group_by(question)%>%
  summarize(agree = sum(response=="Agree",na.rm=T)/n(),
            strongly_agree = sum(response=="Strongly agree",na.rm=T)/n(),
            neutral = sum(response=="Neutral",na.rm=T)/n(),
            disagree = sum(response=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(response=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(response=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=question)) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="General Attitude", 
       y="Percentage of respondents",
       title="Sentiment on TB among CBOs reporting none for minority status Q") +
  scale_x_discrete(labels = c("higher quality event", "positive impact", "purchase tool", "reduce time", "store tool")) +
  scale_fill_manual("Response", values = c("strongly_agree" = "#C2B089", "agree" = "#ECD778", 
                                         "neutral" = "#CCDCD6", "disagree" = "#728E9D", 
                                         "strongly_disagree" =  "#314D59", "N_A" = "#265999"))
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#The ToolBank (TB) has positively impacted our CBO by reducing costs related to purchasing or renting tools and equipment
data <- data%>%
  mutate(top_exec_minority = str_detect(di_mled,"Our top executive position is held by a minority."),
         maj_prog_recip_minority = str_detect(di_mled,"More than 50% of program recipients are minorities"),
         none = str_detect(di_mled,"None of the above"),
         maj_board_minority = str_detect(di_mled,"More than 50% of our board is made up of minorities"),
         )

                                                                                                                                    
# sentiments of top exec minority
data%>%
  filter(top_exec_minority==TRUE)%>%
  pivot_longer(cols=att_purtool:att_posimpact,names_to="question",values_to="response")%>%
  group_by(question)%>%
  summarize(agree = sum(response=="Agree",na.rm=T)/n(),
            strongly_agree = sum(response=="Strongly agree",na.rm=T)/n(),
            neutral = sum(response=="Neutral",na.rm=T)/n(),
            disagree = sum(response=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(response=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(response=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=question)) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="General Attitude", 
       y="Percentage of respondants",
       title="Sentiment on TB among CBOs w/ top exec. a minority") +
  scale_x_discrete(labels = c("higher quality event", "positive impact", "purchase tool", "reduce time", "store tool"))

# sentiments of CBOS w "More than 50% of program recipients are minorities"
data%>%
  filter(maj_prog_recip_minority==TRUE)%>%
  pivot_longer(cols=att_purtool:att_posimpact,names_to="question",values_to="response")%>%
  group_by(question)%>%
  summarize(agree = sum(response=="Agree",na.rm=T)/n(),
            strongly_agree = sum(response=="Strongly agree",na.rm=T)/n(),
            neutral = sum(response=="Neutral",na.rm=T)/n(),
            disagree = sum(response=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(response=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(response=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=question)) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="General Attitude", 
       y="Percentage of respondants",
       title="Sentiment on TB among CBOs w/ 50%+ program recipients are minorities") +
  scale_x_discrete(labels = c("higher quality event", "positive impact", "purchase tool", "reduce time", "store tool"))

#sentiment of CBOs w "More than 50% of our board is made up of minorities"
data%>%
  filter(maj_board_minority==TRUE)%>%
  pivot_longer(cols=att_purtool:att_posimpact,names_to="question",values_to="response")%>%
  group_by(question)%>%
  summarize(agree = sum(response=="Agree",na.rm=T)/n(),
            strongly_agree = sum(response=="Strongly agree",na.rm=T)/n(),
            neutral = sum(response=="Neutral",na.rm=T)/n(),
            disagree = sum(response=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(response=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(response=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=question)) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="General Attitude", 
       y="Percentage of respondants",
       title="Sentiment on TB among CBOs w/ 50%+ board members are minorities") +
  scale_x_discrete(labels = c("higher quality event", "positive impact", "purchase tool", "reduce time", "store tool"))

# sentiments of CBOs who responded "None of the above"
data%>%
  filter(none==TRUE)%>%
  pivot_longer(cols=att_purtool:att_posimpact,names_to="question",values_to="response")%>%
  group_by(question)%>%
  summarize(agree = sum(response=="Agree",na.rm=T)/n(),
            strongly_agree = sum(response=="Strongly agree",na.rm=T)/n(),
            neutral = sum(response=="Neutral",na.rm=T)/n(),
            disagree = sum(response=="Disagree",na.rm=T)/n(),
            strongly_disagree = sum(response=="Strongly disagree",na.rm=T)/n(),
            N_A = sum(response=="N/A",na.rm=T)/n())%>%
  pivot_longer(agree:N_A, 
               names_to= "Response", 
               values_to = "Percentage")%>%
  mutate(Response = factor(Response, levels = c("strongly_agree",
                                                "agree",
                                                "neutral", 
                                                "disagree",
                                                "strongly_disagree", 
                                                 "N_A")))%>%
  ggplot(aes(fill=Response,
             y=Percentage, 
             x=question)) + 
    geom_bar(position="stack", 
             stat="identity")+
  labs(x="General Attitude", 
       y="Percentage of respondants",
       title="Sentiment on TB among CBOs reporting none for minority status Q") +
  scale_x_discrete(labels = c("higher quality event", "positive impact", "purchase tool", "reduce time", "store tool"))
```

**Findings:**

- Respondents' attitude towards the TB are similar across organizations with different minority status. Part of the reason may be that respondents in these categories overlap with each other
- Attitudes of respondents from organizations with no minority status are more fluctuated, which is likely related to the small sample size for that group


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
### Response analysis
#overall table:
#creating a table to give these summary stats
#n respondants 
num_resp <- nrow(data)

#att_purtool: the ToolBank (TB) has positively impacted our CBO by reducing costs related to purchasing or renting tools and equipment
table_att_purtool<- as.data.frame(table(data$att_purtool))
list_of_names <- unique(as.character(table_att_purtool$Var1))
list_of_counts <- c(as.character(table_att_purtool$Freq))


count_purtool_s_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly disagree"))]
count_purtool_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Disagree"))]
count_purtool_n_initial <- list_of_counts[as.numeric(which(list_of_names=="Neutral"))]
count_purtool_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Agree"))]
count_purtool_s_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly agree"))]
count_purtool_na_initial <- list_of_counts[as.numeric(which(list_of_names=="N/A"))]

#strongly disagree
if(is_empty(count_purtool_s_d_initial)){
    count_purtool_s_d <- 0
    pct_purtool_s_d <- 0
}else{
    count_purtool_s_d <- as.numeric(count_purtool_s_d_initial)
    pct_purtool_s_d <- round(count_purtool_s_d/num_resp*100,1)
}
#disagree
if(is_empty(count_purtool_d_initial)){
    count_purtool_d <- 0
    pct_purtool_d <- 0
}else{
    count_purtool_d <-  as.numeric(count_purtool_d_initial)
    pct_purtool_d <- round(count_purtool_d/num_resp*100,1)
}
#neutral
if(is_empty(count_purtool_n_initial)){
    count_purtool_n <- 0
    pct_purtool_n <- 0
}else{
    count_purtool_n <-  as.numeric(count_purtool_n_initial)
    pct_purtool_n <- round(count_purtool_n/num_resp*100,1)
}
#agree
if(is_empty(count_purtool_a_initial)){
    count_purtool_a <- 0
    pct_purtool_a <- 0
}else{
    count_purtool_a <-  as.numeric(count_purtool_a_initial)
    pct_purtool_a <- round(count_purtool_a/num_resp*100,1)
}
#stronngly agree
if(is_empty(count_purtool_s_a_initial)){
    count_purtool_s_a <- 0
    pct_purtool_s_a <- 0
}else{
    count_purtool_s_a <-  as.numeric(count_purtool_s_a_initial)
    pct_purtool_s_a <- round(count_purtool_s_a/num_resp*100,1)
}
#na
if(is_empty(count_purtool_na_initial)){
    count_purtool_na <- 0
    pct_purtool_na <- 0
}else{
    count_purtool_na <- as.numeric(count_purtool_na_initial)
    pct_purtool_na <- round(count_purtool_na/num_resp*100,1)
}




#att_strtool: the TB has positively impacted our CBO by reducing costs related to storing tools and equipment
table_att_strtool<- as.data.frame(table(data$att_strtool))
list_of_names <- unique(as.character(table_att_strtool$Var1))
list_of_counts <- c(as.character(table_att_strtool$Freq))


count_strtool_s_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly disagree"))]
count_strtool_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Disagree"))]
count_strtool_n_initial <- list_of_counts[as.numeric(which(list_of_names=="Neutral"))]
count_strtool_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Agree"))]
count_strtool_s_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly agree"))]
count_strtool_na_initial <- list_of_counts[as.numeric(which(list_of_names=="N/A"))]

#strongly disagree
if(is_empty(count_strtool_s_d_initial)){
    count_strtool_s_d <- 0
    pct_strtool_s_d <- 0
}else{
    count_strtool_s_d <- as.numeric(count_strtool_s_d_initial)
    pct_strtool_s_d <- round(count_strtool_s_d/num_resp*100,1)
}
#disagree
if(is_empty(count_strtool_d_initial)){
    count_strtool_d <- 0
    pct_strtool_d <- 0
}else{
    count_strtool_d <-  as.numeric(count_strtool_d_initial)
    pct_strtool_d <- round(count_strtool_d/num_resp*100,1)
}
#neutral
if(is_empty(count_strtool_n_initial)){
    count_strtool_n <- 0
    pct_strtool_n <- 0
}else{
    count_strtool_n <-  as.numeric(count_strtool_n_initial)
    pct_strtool_n <- round(count_strtool_n/num_resp*100,1)
}
#agree
if(is_empty(count_strtool_a_initial)){
    count_strtool_a <- 0
    pct_strtool_a <- 0
}else{
    count_strtool_a <-  as.numeric(count_strtool_a_initial)
    pct_strtool_a <- round(count_strtool_a/num_resp*100,1)
}
#stronngly agree
if(is_empty(count_strtool_s_a_initial)){
    count_strtool_s_a <- 0
    pct_strtool_s_a <- 0
}else{
    count_strtool_s_a <-  as.numeric(count_strtool_s_a_initial)
    pct_strtool_s_a <- round(count_strtool_s_a/num_resp*100,1)
}
#na
if(is_empty(count_strtool_na_initial)){
    count_strtool_na <- 0
    pct_strtool_na <- 0
}else{
    count_strtool_na <- as.numeric(count_strtool_na_initial)
    pct_strtool_na <- round(count_strtool_na/num_resp*100,1)
}

#att_redtime: theTB has positively impacted our CBO by reducing staff time to complete maintenance/projects
table_att_redtime<- as.data.frame(table(data$att_redtime))
list_of_names <- unique(as.character(table_att_redtime$Var1))
list_of_counts <- c(as.character(table_att_redtime$Freq))


count_redtime_s_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly disagree"))]
count_redtime_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Disagree"))]
count_redtime_n_initial <- list_of_counts[as.numeric(which(list_of_names=="Neutral"))]
count_redtime_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Agree"))]
count_redtime_s_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly agree"))]
count_redtime_na_initial <- list_of_counts[as.numeric(which(list_of_names=="N/A"))]

#strongly disagree
if(is_empty(count_redtime_s_d_initial)){
    count_redtime_s_d <- 0
    pct_redtime_s_d <- 0
}else{
    count_redtime_s_d <- as.numeric(count_redtime_s_d_initial)
    pct_redtime_s_d <- round(count_redtime_s_d/num_resp*100,1)
}
#disagree
if(is_empty(count_redtime_d_initial)){
    count_redtime_d <- 0
    pct_redtime_d <- 0
}else{
    count_redtime_d <-  as.numeric(count_redtime_d_initial)
    pct_redtime_d <- round(count_redtime_d/num_resp*100,1)
}
#neutral
if(is_empty(count_redtime_n_initial)){
    count_redtime_n <- 0
    pct_redtime_n <- 0
}else{
    count_redtime_n <-  as.numeric(count_redtime_n_initial)
    pct_redtime_n <- round(count_redtime_n/num_resp*100,1)
}
#agree
if(is_empty(count_redtime_a_initial)){
    count_redtime_a <- 0
    pct_redtime_a <- 0
}else{
    count_redtime_a <-  as.numeric(count_redtime_a_initial)
    pct_redtime_a <- round(count_redtime_a/num_resp*100,1)
}
#stronngly agree
if(is_empty(count_redtime_s_a_initial)){
    count_redtime_s_a <- 0
    pct_redtime_s_a <- 0
}else{
    count_redtime_s_a <-  as.numeric(count_redtime_s_a_initial)
    pct_redtime_s_a <- round(count_redtime_s_a/num_resp*100,1)
}
#na
if(is_empty(count_redtime_na_initial)){
    count_redtime_na <- 0
    pct_redtime_na <- 0
}else{
    count_redtime_na <- as.numeric(count_redtime_na_initial)
    pct_redtime_na <- round(count_redtime_na/num_resp*100,1)
}


#att_evquality:  "the Tools made available through the TB allow our CBO to complete higher quality events/projects without additional funding
table_att_evquality<- as.data.frame(table(data$att_evquality))
list_of_names <- unique(as.character(table_att_evquality$Var1))
list_of_counts <- c(as.character(table_att_evquality$Freq))


count_evquality_s_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly disagree"))]
count_evquality_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Disagree"))]
count_evquality_n_initial <- list_of_counts[as.numeric(which(list_of_names=="Neutral"))]
count_evquality_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Agree"))]
count_evquality_s_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly agree"))]
count_evquality_na_initial <- list_of_counts[as.numeric(which(list_of_names=="N/A"))]

#strongly disagree
if(is_empty(count_evquality_s_d_initial)){
    count_evquality_s_d <- 0
    pct_evquality_s_d <- 0
}else{
    count_evquality_s_d <- as.numeric(count_evquality_s_d_initial)
    pct_evquality_s_d <- round(count_evquality_s_d/num_resp*100,1)
}
#disagree
if(is_empty(count_evquality_d_initial)){
    count_evquality_d <- 0
    pct_evquality_d <- 0
}else{
    count_evquality_d <-  as.numeric(count_evquality_d_initial)
    pct_evquality_d <- round(count_evquality_d/num_resp*100,1)
}
#neutral
if(is_empty(count_evquality_n_initial)){
    count_evquality_n <- 0
    pct_evquality_n <- 0
}else{
    count_evquality_n <-  as.numeric(count_evquality_n_initial)
    pct_evquality_n <- round(count_evquality_n/num_resp*100,1)
}
#agree
if(is_empty(count_evquality_a_initial)){
    count_evquality_a <- 0
    pct_evquality_a <- 0
}else{
    count_evquality_a <-  as.numeric(count_evquality_a_initial)
    pct_evquality_a <- round(count_evquality_a/num_resp*100,1)
}
#stronngly agree
if(is_empty(count_evquality_s_a_initial)){
    count_evquality_s_a <- 0
    pct_evquality_s_a <- 0
}else{
    count_evquality_s_a <-  as.numeric(count_evquality_s_a_initial)
    pct_evquality_s_a <- round(count_evquality_s_a/num_resp*100,1)
}
#na
if(is_empty(count_evquality_na_initial)){
    count_evquality_na <- 0
    pct_evquality_na <- 0
}else{
    count_evquality_na <- as.numeric(count_evquality_na_initial)
    pct_evquality_na <- round(count_evquality_na/num_resp*100,1)
}

#att_posimpact:  TB has positively impacted our CBO 
table_att_posimpact<- as.data.frame(table(data$att_posimpact))
list_of_names <- unique(as.character(table_att_posimpact$Var1))
list_of_counts <- c(as.character(table_att_posimpact$Freq))


count_posimpact_s_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly disagree"))]
count_posimpact_d_initial <- list_of_counts[as.numeric(which(list_of_names=="Disagree"))]
count_posimpact_n_initial <- list_of_counts[as.numeric(which(list_of_names=="Neutral"))]
count_posimpact_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Agree"))]
count_posimpact_s_a_initial <- list_of_counts[as.numeric(which(list_of_names=="Strongly agree"))]
count_posimpact_na_initial <- list_of_counts[as.numeric(which(list_of_names=="N/A"))]

#strongly disagree
if(is_empty(count_posimpact_s_d_initial)){
    count_posimpact_s_d <- 0
    pct_posimpact_s_d <- 0
}else{
    count_posimpact_s_d <- as.numeric(count_posimpact_s_d_initial)
    pct_posimpact_s_d <- round(count_posimpact_s_d/num_resp*100,1)
}
#disagree
if(is_empty(count_posimpact_d_initial)){
    count_posimpact_d <- 0
    pct_posimpact_d <- 0
}else{
    count_posimpact_d <-  as.numeric(count_posimpact_d_initial)
    pct_posimpact_d <- round(count_posimpact_d/num_resp*100,1)
}
#neutral
if(is_empty(count_posimpact_n_initial)){
    count_posimpact_n <- 0
    pct_posimpact_n <- 0
}else{
    count_posimpact_n <-  as.numeric(count_posimpact_n_initial)
    pct_posimpact_n <- round(count_posimpact_n/num_resp*100,1)
}
#agree
if(is_empty(count_posimpact_a_initial)){
    count_posimpact_a <- 0
    pct_posimpact_a <- 0
}else{
    count_posimpact_a <-  as.numeric(count_posimpact_a_initial)
    pct_posimpact_a <- round(count_posimpact_a/num_resp*100,1)
}
#stronngly agree
if(is_empty(count_posimpact_s_a_initial)){
    count_posimpact_s_a <- 0
    pct_posimpact_s_a <- 0
}else{
    count_posimpact_s_a <-  as.numeric(count_posimpact_s_a_initial)
    pct_posimpact_s_a <- round(count_posimpact_s_a/num_resp*100,1)
}
#na
if(is_empty(count_posimpact_na_initial)){
    count_posimpact_na <- 0
    pct_posimpact_na <- 0
}else{
    count_posimpact_na <- as.numeric(count_posimpact_na_initial)
    pct_posimpact_na <- round(count_posimpact_na/num_resp*100,1)
}

```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}

#table summarizing demographic info
output_continuous <- matrix(c(
  
# att_purtool:"TB has pos. impacted our CBO by reducing costs related to purchasing or renting tools and equipment",
  # "# Strongly Agree (%)", 
  paste0(count_purtool_s_a," (",pct_purtool_s_a,"%)"),
  # "# Agree (%)",
  paste0(count_purtool_a," (",pct_purtool_a,"%)"),
  # "# Neutral (%)",
  paste0(count_purtool_n," (",pct_purtool_n,"%)"),
  # "# Disagree (%)",
  paste0(count_purtool_d," (",pct_purtool_d,"%)"),
  # "# Strongly Disagree (%)",
  paste0(count_purtool_s_d," (",pct_purtool_s_d,"%)"),
  # "# N/A (%)"
  paste0(count_purtool_na," (",pct_purtool_na,"%)"),
  
# att_strtool:"TB has pos. impacted our CBO by reducing costs related to storing tools and equipment",
  # "# Strongly Agree (%)", 
  paste0(count_strtool_s_a," (",pct_strtool_s_a,"%)"),
  # "# Agree (%)",
  paste0(count_strtool_a," (",pct_strtool_a,"%)"),
  # "# Neutral (%)",
  paste0(count_strtool_n," (",pct_strtool_n,"%)"),
  # "# Disagree (%)",
  paste0(count_strtool_d," (",pct_strtool_d,"%)"),
  # "# Strongly Disagree (%)",
  paste0(count_strtool_s_d," (",pct_strtool_s_d,"%)"),
  # "# N/A (%)"
  paste0(count_strtool_na," (",pct_strtool_na,"%)"),

# att_redtime:"TB has pos. impacted our CBO by reducing staff time to complete maintenance/projects",
  # "# Strongly Agree (%)", 
  paste0(count_redtime_s_a," (",pct_redtime_s_a,"%)"),
  # "# Agree (%)",
  paste0(count_redtime_a," (",pct_redtime_a,"%)"),
  # "# Neutral (%)",
  paste0(count_redtime_n," (",pct_redtime_n,"%)"),
  # "# Disagree (%)",
  paste0(count_redtime_d," (",pct_redtime_d,"%)"),
  # "# Strongly Disagree (%)",
  paste0(count_redtime_s_d," (",pct_redtime_s_d,"%)"),
  # "# N/A (%)"
  paste0(count_redtime_na," (",pct_redtime_na,"%)"),
# att_evquality: "the Tools made available through the TB allow our CBO to complete higher quality events/projects without additional funding",
  # "# Strongly Agree (%)", 
  paste0(count_evquality_s_a," (",pct_evquality_s_a,"%)"),
  # "# Agree (%)",
  paste0(count_evquality_a," (",pct_evquality_a,"%)"),
  # "# Neutral (%)",
  paste0(count_evquality_n," (",pct_evquality_n,"%)"),
  # "# Disagree (%)",
  paste0(count_evquality_d," (",pct_evquality_d,"%)"),
  # "# Strongly Disagree (%)",
  paste0(count_evquality_s_d," (",pct_evquality_s_d,"%)"),
  # "# N/A (%)"
  paste0(count_evquality_na," (",pct_evquality_na,"%)"),

# att_posimpact: "TB has pos. impacted our CBO"
  # "# Strongly Agree (%)", 
  paste0(count_posimpact_s_a," (",pct_posimpact_s_a,"%)"),
  # "# Agree (%)",
  paste0(count_posimpact_a," (",pct_posimpact_a,"%)"),
  # "# Neutral (%)",
  paste0(count_posimpact_n," (",pct_posimpact_n,"%)"),
  # "# Disagree (%)",
  paste0(count_posimpact_d," (",pct_posimpact_d,"%)"),
  # "# Strongly Disagree (%)",
  paste0(count_posimpact_s_d," (",pct_posimpact_s_d,"%)"),
  # "# N/A (%)"
  paste0(count_posimpact_na," (",pct_posimpact_na,"%)")


),

         ncol = 6, byrow = TRUE)

output_continuous%>% 
  addHtmlTableStyle(col.columns = c("none", "#F7F7F7"),
                    col.rgroup = c("none", "#F5FBFF")
                    )%>% 
  htmlTable(header =  c("#Strongly Agree (%)", 
                        "#Agree (%)",
                        "#Neutral (%)",
                        "#Disagree (%)",
                        "#Strongly Disagree (%)",
                        "#N/A (%)"),
            rnames = c(
"TB has pos. impacted our CBO by reducing costs related to purchasing or renting tools and equipment",
"TB has pos. impacted our CBO by reducing costs related to storing tools and equipment",
"TB has pos. impacted our CBO by reducing staff time to complete maintenance/projects",
"the Tools made available through the TB allow our CBO to complete higher quality events/projects without additional funding",
"TB has pos. impacted our CBO"

            ),
            # rgroup = c("Sentiment "),
            # n.rgroup = c(4),
            caption = "Number, percentages of respondants to sentiment questions"
            )

```


# Section 4: Economic Benefit of the ToolBank

The following section analyses responses to the survey questions regarding the economic benefit of the ToolBank. For these questions, respondents were asked to provide their best estimates rounded to the nearest dollar. This section aimed to quantify the direct impact of the ToolBank on the member CBOs' budgets and fundraising capabilities. This section asked respondents the following questions: 

- If the TB did not exist, how much would you spend purchasing or renting tools and equipment in an average year?
- If the TB did not exist, how much would you spend on storage of tools and equipment in an average year?
- If the TB did not exist, how much would you spend maintaining tools and equipment in an average year?
- Reflecting on your events in the past year: If the TB did not exist, how much funding would your organization allocate to buying, storing, tracking and maintaining your own inventory of tools and equipment?
- In the past year, how many community events did your organization host?
- If there were no TB, how many of your events in the past year would you not have hosted for any reason?
- If there were no TB, how many of your constituents, including volunteers, members, and event attendees, would have been negatively impacted in the past year?

*Note that the responses to all of the following questions in this section are highly skewed. As a result, we recommended reporting sum, medians, or quantiles rather than averages *



**Figure 14: Distribution of money spent purchasing/renting tools/equipment if TB did not exist**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
# Create a vector 
eco_purchase<- data$eco_purchase

# Define a function to calculate the mode
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
# Calculate mean, median, and mode
mean_value <- mean(eco_purchase)
median_value <- median(eco_purchase)
mode_value <- Mode(eco_purchase)
sd_value <- sd(eco_purchase)
q25_value <- quantile(eco_purchase, 0.25)
q75_value <- quantile(eco_purchase, 0.75)
sum_value <- sum(eco_purchase)

# Create a summary table
summary_table_eco_purchase<- data.frame(
  Measure = c("Mean", "Median", "Mode", "sd", "1st quantile", "3rd quantile", "Sum"),
  Value = c(mean_value, median_value, mode_value, sd_value, q25_value, q75_value, sum_value)
)

# Display the summary table
#print(summary_table_eco_purchase)

# Display histogram
hist(eco_purchase, main = NULL, xlab = "spending (dollars)", col = "#265999", border = "white")

#extract info for an overall table
purchase_mean <- mean_value
purchase_med <- median_value
purchase_mod <- mode_value
purchase_sd <- sd_value
purchase_q1 <- q25_value
purchase_q3 <- q75_value
purchase_sum <- sum_value
```



**Figure 15: Distribution of money spent storing tools/equipment if TB did not exist**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
# Create a vector 
eco_storage<- data$eco_storage

# Define a function to calculate the mode
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
# Calculate mean, median, and mode
mean_value <- mean(eco_storage)
median_value <- median(eco_storage)
mode_value <- Mode(eco_storage)
sd_value <- sd(eco_storage)
q25_value <- quantile(eco_storage, 0.25)
q75_value <- quantile(eco_storage, 0.75)
sum_value <- sum(eco_storage)

# Create a summary table
summary_table_eco_storage<- data.frame(
  Measure = c("Mean", "Median", "Mode", "sd", "1st quantile", "3rd quantile", "Sum"),
  Value = c(mean_value, median_value, mode_value, sd_value, q25_value, q75_value, sum_value)
)

# Display the summary table
#print(summary_table_eco_storage)

# Display histogram
hist(eco_storage, main = NULL, xlab = "spending (dollars)", col = "#265999", border = "white")

#extract values for an overall table
storage_mean <- mean_value
storage_med <- median_value
storage_mod <- mode_value
storage_sd <- sd_value
storage_q1 <- q25_value
storage_q3 <- q75_value
storage_sum <- sum_value
```

**Figure 16: Distribution of money spent on tool maintenance if TB did not exist**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
# Create a vector 
eco_maintain<- data$eco_maintain

# Define a function to calculate the mode
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
# Calculate mean, median, and mode
mean_value <- mean(eco_maintain)
median_value <- median(eco_maintain)
mode_value <- Mode(eco_maintain)
sd_value <- sd(eco_maintain)
q25_value <- quantile(eco_maintain, 0.25)
q75_value <- quantile(eco_maintain, 0.75)
sum_value <- sum(eco_maintain)

# Create a summary table
summary_table_eco_maintain<- data.frame(
  Measure = c("Mean", "Median", "Mode", "sd", "1st quantile", "3rd quantile", "Sum"),
  Value = c(mean_value, median_value, mode_value, sd_value, q25_value, q75_value, sum_value)
)

# Display the summary table
#print(summary_table_eco_maintain)

# Display histogram
hist(eco_maintain, main = NULL, xlab = "spending (dollars)", col = "#265999", border = "white")

#extract values for an overall table
maintain_mean <- mean_value
maintain_med <- median_value
maintain_mod <- mode_value
maintain_sd <- sd_value
maintain_q1 <- q25_value
maintain_q3 <- q75_value
maintain_sum <- sum_value
```


**Figure 17: Dist of money spent on all tool/equipment related costs if TB did not exist (past year)**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
# Create a vector 
eco_totalcost<- data$eco_totalcost

# Define a function to calculate the mode
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
# Calculate mean, median, and mode
mean_value <- mean(eco_totalcost)
median_value <- median(eco_totalcost)
mode_value <- Mode(eco_totalcost)
sd_value <- sd(eco_totalcost)
q25_value <- quantile(eco_totalcost, 0.25)
q75_value <- quantile(eco_totalcost, 0.75)
sum_value <- sum(eco_totalcost)

# Create a summary table
summary_table_eco_totalcost<- data.frame(
  Measure = c("Mean", "Median", "Mode", "sd", "1st quantile", "3rd quantile", "Sum"),
  Value = c(mean_value, median_value, mode_value, sd_value, q25_value, q75_value, sum_value)
)

# Display the summary table
#print(summary_table_eco_totalcost)

# Display histogram
hist(eco_totalcost, main = NULL, xlab = "spending (dollars)", col = "#265999", border = "white")

#extract values for an overall table
totalcost_mean <- mean_value
totalcost_med <- median_value
totalcost_mod <- mode_value
totalcost_sd <- sd_value
totalcost_q1 <- q25_value
totalcost_q3 <- q75_value
totalcost_sum <- sum_value
```


**Figure 18: Distribution of total events hosted in past year**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
# Create a vector 
eco_events<- data$eco_events

# Define a function to calculate the mode
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
# Calculate mean, median, and mode
mean_value <- mean(eco_events)
median_value <- median(eco_events)
mode_value <- Mode(eco_events)
sd_value <- sd(eco_events)
q25_value <- quantile(eco_events, 0.25)
q75_value <- quantile(eco_events, 0.75)
sum_value <- sum(eco_events)

# Create a summary table
summary_table_eco_events<- data.frame(
  Measure = c("Mean", "Median", "Mode", "sd", "1st quantile", "3rd quantile", "Sum"),
  Value = c(mean_value, median_value, mode_value, sd_value, q25_value, q75_value, sum_value)
)

# Display the summary table
#print(summary_table_eco_events)

# Display histogram
hist(eco_events, main = NULL, xlab = "count of events", col = "#265999", border = "white")

#extract values for an overall table
events_mean <- mean_value
events_med <- median_value
events_mod <- mode_value
events_sd <- sd_value
events_q1 <- q25_value
events_q3 <- q75_value
events_sum <- sum_value
```


**Figure 19: Distribution of past-year events impossible w/o TB**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
# Create a vector 
eco_nothost<- data$eco_nothost

# Define a function to calculate the mode
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
# Calculate mean, median, and mode
mean_value <- mean(eco_nothost)
median_value <- median(eco_nothost)
mode_value <- Mode(eco_nothost)
sd_value <- sd(eco_nothost)
q25_value <- quantile(eco_nothost, 0.25)
q75_value <- quantile(eco_nothost, 0.75)
sum_value <- sum(eco_nothost)

# Create a summary table
summary_table_eco_nothost<- data.frame(
  Measure = c("Mean", "Median", "Mode", "sd", "1st quantile", "3rd quantile", "Sum"),
  Value = c(mean_value, median_value, mode_value, sd_value, q25_value, q75_value, sum_value)
)
# Display the summary table
#print(summary_table_eco_nothost)

# Display histogram
hist(eco_nothost, main = NULL, xlab = "count of events", col = "#265999", border = "white")

nothost_mean <- mean_value
nothost_med <- median_value
nothost_mod <- mode_value
nothost_sd <- sd_value
nothost_q1 <- q25_value
nothost_q3 <- q75_value
nothost_sum <- sum_value
```


**Figure 20: Distribution of % of past-year events impossible w/o TB**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
data$eco_nothost_pct_calc = data$eco_nothost/data$eco_events
eco_nothost_pct_calc = data$eco_nothost_pct_calc
# Define a function to calculate the mode
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
# Calculate mean, median, and mode
mean_value <- mean(eco_nothost_pct_calc)
median_value <- median(eco_nothost_pct_calc)
mode_value <- Mode(eco_nothost_pct_calc)
sd_value <- sd(eco_nothost_pct_calc)
q25_value <- quantile(eco_nothost_pct_calc, 0.25)
q75_value <- quantile(eco_nothost_pct_calc, 0.75)
sum_value <- sum(eco_nothost_pct_calc)


# Create a summary table
summary_table_eco_nothost_pct_calc<- data.frame(
  Measure = c("Mean", "Median", "Mode"),
  Value = c(mean_value, median_value, mode_value)
)

# Display the summary table
#print(summary_table_eco_nothost_pct_calc)

# Display histogram
hist(eco_nothost_pct_calc*100, main = NULL, xlab = "Percentage(%)", col = "#265999", border = "white")

nothost_pct_calc_mean <- mean_value
nothost_pct_calc_med <- median_value
nothost_pct_calc_mod <- mode_value
nothost_pct_calc_sd <- sd_value
nothost_pct_calc_q1 <- q25_value
nothost_pct_calc_q3 <- q75_value
nothost_pct_calc_sum <- sum_value
```

**Figure 21: Distribution of negatively impacted constituents if TB did not exist (past year)**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
# Create a vector 
eco_constit<- data$eco_constit

# Define a function to calculate the mode
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
# Calculate mean, median, and mode
max_value <- max(eco_constit)
min_value <- min(eco_constit)
range_value <- max(eco_constit)- min(eco_constit)
mean_value <- mean(eco_constit)
median_value <- median(eco_constit)
mode_value <- Mode(eco_constit)
sd_value <- sd(eco_constit)
q25_value <- quantile(eco_constit, 0.25)
q75_value <- quantile(eco_constit, 0.75)
sum_value <- sum(eco_constit)

# Create a summary table
summary_table_eco_constit<- data.frame(
  Measure = c("Mean", "Median", "Mode", "sd", "1st quantile", "3rd quantile", "Sum"),
  Value = c(mean_value, median_value, mode_value, sd_value, q25_value, q75_value, sum_value)
)

# Display the summary table
#print(summary_table_eco_constit)

# Display histogram
hist(eco_constit, main = NULL, xlab = "count", col = "#265999", border = "white")

constit_mean <- mean_value
constit_med <- median_value
constit_mod <- mode_value
constit_sd <- sd_value
constit_q1 <- q25_value
constit_q3 <- q75_value
constit_sum <- sum_value
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
#Calculated: 
#Reflecting on your events in the past year, how many events did your organization host?
#If there were no TB, how many of your events in the past year would you not have been able to host?
#What percentage of the events hosted last year did the TB help make possible?
#put all this into one table:


output_continuous <- matrix(c(
# "on Purchasing or renting tools and equipment",
  #"Mean"
round(purchase_mean),
  #"25th quantile", 
round(purchase_q1),
  #"Median", 
round(purchase_med),
  #"Mode",
round(purchase_mod),
  #"75th quantile",
round(purchase_q3),
  #"Standard deviation"
round(purchase_sd),
  #"Sum"
round(purchase_sum),

# "on storage of tools and equipment",
  #"Mean"
round(storage_mean),
  #"25th quantile", 
round(storage_q1),
  #"Median", 
round(storage_med),
  #"Mode",
round(storage_mod),
  #"75th quantile",
round(storage_q3),
  #"Standard deviation"
round(storage_sd),
#"Sum"
round(storage_sum),

# "on maintenance of tools and equipment",
  #"Mean"
round(maintain_mean),
  #"25th quantile", 
round(maintain_q1),
  #"Median", 
round(maintain_med),
  #"Mode",
round(maintain_mod),
  #"75th quantile",
round(maintain_q3),
  #"Standard deviation"
round(maintain_sd),
#"Sum"
round(maintain_sum),

# "on buying, storing, tracking and maintaining own tool+equiptment inventory",
  #"Mean"
round(totalcost_mean),
  #"25th quantile", 
round(totalcost_q1),
  #"Median", 
round(totalcost_med),
  #"Mode",
round(totalcost_mod),
  #"75th quantile",
round(totalcost_q3),
  #"Standard deviation"
round(totalcost_sd),
#"Sum"
round(totalcost_sum),
# "# events that would have been impossible in past year",
  #"Mean"
round(nothost_mean),
  #"25th quantile", 
round(nothost_q1),
  #"Median", 
round(nothost_med),
  #"Mode",
round(nothost_mod),
  #"75th quantile",
round(nothost_q3),
  #"Standard deviation"
round(nothost_sd),
#"Sum"
round(nothost_sum),
# "% of CBO's total events that would have been impossible in past year",
  #"Mean"
round(nothost_pct_calc_mean*100),
  #"25th quantile", 
round(nothost_pct_calc_q1*100),
  #"Median", 
round(nothost_pct_calc_med*100),
  #"Mode",
round(nothost_pct_calc_mod*100),
  #"75th quantile",
round(nothost_pct_calc_q3*100),
  #"Standard deviation"
round(nothost_pct_calc_sd*100),
#"Sum"
round(nothost_pct_calc_sum*100),
# "# constituents that would have been negatively impacted in the past year "
  #"Mean"
round(constit_mean),
  #"25th quantile", 
round(constit_q1),
  #"Median", 
round(constit_med),
  #"Mode",
round(constit_mod),
  #"75th quantile",
round(constit_q3),
  #"Standard deviation"
round(constit_sd),
#"Sum"
round(constit_sum)
                              
                              ),

         ncol = 7, byrow = TRUE)

library(htmlTable)
output_continuous%>% 
  addHtmlTableStyle(col.columns = c("none", "#F7F7F7",
                                    "none", "#F7F7F7",
                                    "none", "#F7F7F7"))%>% 
  htmlTable(header =  c("Mean","25th quantile", "Median", "Mode","75th quantile","Standard deviation", "Sum"),
            rnames = c("on Purchasing or renting tools and equipment",
                       "on storage of tools and equipment",
                       "on maintenance of tools and equipment",
                       "on buying, storing, tracking and maintaining own tool+equiptment inventory",
                       "# events that would have been impossible in past year",
                       "% of CBO's total events that would have been impossible in past year",
                       "# constituents that would have been negatively impacted in the past year "
            ),
            rgroup = c("Money That Would Have Been Spent if TB Did Not Exist*",
                       "# Events/People Impacted If TB Did Not Exist"),
            n.rgroup = c(4,3),
            caption = "Table 4: Impact on CBO if TB did not exists",
            tfoot = "*in US dollars"
            )

```

**Figures 22a-d: Distribution of events possible through TB by minority status**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
data%>%
  group_by(row_number())%>%
  mutate(`Percent of events posible by TB (%)` = round(eco_nothost/eco_events*100,1))%>%
  ggplot(aes(x=`Percent of events posible by TB (%)`))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(title="Percentage of events in the least year made posible by TB")
#events in past year: eco_events

#stratify by minority status
data%>%
  filter(top_exec_minority==TRUE)%>%
  group_by(row_number())%>%
  mutate(`Percent of events posible by TB (%)` = round(eco_nothost/eco_events*100,1))%>%
  ggplot(aes(x=`Percent of events posible by TB (%)`))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(title="% events through TB: among CBOs w/ top exec a minority")
data%>%
  filter(maj_prog_recip_minority==TRUE)%>%
  group_by(row_number())%>%
  mutate(`Percent of events posible by TB (%)` = round(eco_nothost/eco_events*100,1))%>%
  ggplot(aes(x=`Percent of events posible by TB (%)`))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(title="% events through TB: among CBOs w/ 50%+ prog. recipients minorities")
data%>%
  filter(maj_board_minority==TRUE)%>%
  group_by(row_number())%>%
  mutate(`Percent of events posible by TB (%)` = round(eco_nothost/eco_events*100,1))%>%
  ggplot(aes(x=`Percent of events posible by TB (%)`))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(title="% events through TB: among CBOs w/ 50%+ board members minorities")



# data%>%
#   group_by(row_number())%>%
#   mutate(`Percent of events posible by TB` = round(eco_nothost/eco_events*100,1))%>%
#   ungroup()%>%
#   summarize(`Average % of a CBO's events possible through TB in past year` = mean(`Percent of events posible by TB`))
```

**Findings:**

- In an average year, the ToolBank helps to save money in buying, storing, tracking, and maintaining tools or equipments for the 45 respondents a sum value of \$304, 700, among which purchasing tools and equipments cost our partner CBO the most with \$226,300 (74.3%)
- In the past year, the ToolBank helps to save money in buying, storing, tracking, and maintaining tools or equipments for the 45 respondents a sum value of \$113,720
- Half of the respondents reported that at least 35% of their events would have been impossible without the help of the ToolBank
- A total of 280 events would have been impossible if the ToolBank did not exist
- Half of the respondents reported that at least 150 of their constituents (volunteers, members, and event attendees) would have been negatively impacted without the help of the ToolBank
- A total of 58,790 constituents (volunteers, members, and event attendees) of our CBO partners would haven been negatively impacted without the help of the ToolBank

# Section 5: Community Impact of the Tool Bank
The following section summarizes the community impact of the ToolBank, as reported by survey respondents. This section aims to quantify the indirect ways that the ToolBank may impact CBOs and the community by reducing barriers and costs related to accessing tools and equipment. This section analyzes responded from the following survey questions: 

- With the money you have saved on purchasing, storing, and maintaining tools and equipment through the TB, what have you been able to accomplish?
-Without the TB, what would you no longer be able to fund?
- If you answered 'staff', how many positions would be impacted?
- If you answered 'projects', how many projects would be impacted?
- If other, please quantify the impact:
- Without the TB, which of the following are ways that your community events would be impacted? (check all that apply: Quantity, Quality, Diversity, Consistency)


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#Question: With the money that you have saved on purchasing, storing, and maintaining tools and equipment, what have you been able to accomplish
sum_table = data.frame(cbind(choices = c("Hired additional staff positions",
                                         "Hosted additional projects or events",
                                         "other"),
                             frequency = round(c(nrow(data[data$ci_exaccomp_stf == 1,]),
                                            nrow(data[data$ci_exaccomp_prj == 1,]),
                                            nrow(data[!is.na(data$ci_exaccomp_otr),])),3),
                             percentage = round(c(nrow(data[data$ci_exaccomp_stf == 1,])/nrow(data),
                                            nrow(data[data$ci_exaccomp_prj == 1,])/nrow(data),
                                            nrow(data[!is.na(data$ci_exaccomp_otr),])/nrow(data)),3)))
sum_table

with_money_hire_staff_freq <- sum_table[1,2]
with_money_hire_staff_pct <- round(as.numeric(sum_table[1,3])*100,1)
more_proj_freq <- sum_table[2,2]
more_proj_pct <- round(as.numeric(sum_table[2,3])*100,1)
other_freq <- sum_table[3,2]
other_pct <- round(as.numeric(sum_table[3,3])*100,1)
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#Question: Without the TB, what would you no longer be able to fund?
sum_table = data.frame(cbind(choices = c("Staff",
                                         "Projects",
                                         "other"),
                             frequency = round(c(nrow(data[data$ci_cutfund_stf == 1,]),
                                            nrow(data[data$ci_cutfund_prj == 1,]),
                                            nrow(data[!is.na(data$ci_cutfund_otr),])),3),
                             percentage = round(c(nrow(data[data$ci_cutfund_stf == 1,])/nrow(data),
                                            nrow(data[data$ci_cutfund_prj == 1,])/nrow(data),
                                            nrow(data[!is.na(data$ci_cutfund_otr),])/nrow(data)),3)))
sum_table


without_money_hire_staff_freq <- sum_table[1,2]
without_money_hire_staff_pct <- round(as.numeric(sum_table[1,3])*100,1)
without_proj_freq <- sum_table[2,2]
without_proj_pct <- round(as.numeric(sum_table[2,3])*100,1)
without_other_freq <- sum_table[3,2]
without_other_pct <- round(as.numeric(sum_table[3,3])*100,1)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE, include=F}
#Among partners indicated certain effect, what is the average quantified effects
mean(data$ci_staff, na.rm = T)
sd(data$ci_staff, na.rm = T)
mean(data$ci_project, na.rm = T)
sd(data$ci_project, na.rm = T)
```

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
output_continuous <- matrix(c(
# "Hired more staff",
#   #
with_money_hire_staff_freq, 
#   %
paste0(with_money_hire_staff_pct,"%"),
# "Hosted additional projects/events",
#
more_proj_freq,
#%
paste0(more_proj_pct,"%"),
# "Other",
##
other_freq,
#%
paste0(other_pct,"%"),
# "Cut staff funding",
##
without_money_hire_staff_freq,
#%
paste0(without_money_hire_staff_pct,"%"),
# "Cut project funding",
##
without_proj_freq,
#%
paste0(without_proj_pct,"%"),
# "Other"
##
without_other_freq,
#%
paste0(without_other_pct,"%")

),

         ncol = 2, byrow = TRUE)

library(htmlTable)
output_continuous%>% 
  addHtmlTableStyle(col.columns = c("none", "#F7F7F7"))%>% 
  htmlTable(header =  c("# Respondents", "% Respondents"),
            rnames = c("Hired more staff",
                       "Hosted additional projects/events",
                       "Other",
                       "Cut staff funding",
                       "Cut project funding",
                       "Other"
            ),
            rgroup = c("Accomplishments through money saved through TB",
                       "Where funding would be cut if TB did not exist"),
            n.rgroup = c(3,3),
            caption = "Table 5: Number and Percentage of Respondants Reporting Impacts of Funds Saved "
            )
```


**Findings:**

- More than half of the respondents agree that they can host additional projects or event with the fundings the ToolBanks helped to save (60.0%) and would need to cut project fundings if the ToolBank did not exist (57.8%).
- Funding related to staff positions were less impacted by the ToolBank action.
- 24.4% respondents reported the fundings the ToolBank helps them to save make them able to achieve accomplishments other than staff positions and projects.
- 15.6% respondents reported that they need to cut fundings in items other than staff positions and projects if the ToolBank did not exist.

# Section 6: Fundraising Impact of the ToolBank 

The following section aims to quantify the impact that the ToolBank may have on CBOs' ability to host specific events, including fundraising. This section analyses the following survey questions: 

- Which of the following types of events have TB tools and equipment helped your CBO complete?

- If you use the TB to support your fundraising events, in an average year, what have been the outcomes of these fundraising events?

- To your best estimate, what percent of your event expense budget was saved by using TB equipment at your event? Example: "We raised $20,000 at our annual fundraiser and hosted 150 people."



The following plots address the question whether there is a relationship between money saved through the Toolbank and attitude towards the Toolbank

**Figures 23a-e: Money saved through TB (past year) by attitude towards TB**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
data%>%
  mutate(att_posimpact = factor(att_posimpact, levels = c("Strongly agree",
                                                "Agree",
                                                "Neutral", 
                                                "Disagree",
                                                "Strongly disagree", 
                                                 "N/A")))%>%    
  ggplot(aes(x=att_posimpact, y=eco_totalcost))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(x="Agreement with TB has positively impacted CBO",
       y= "Money",
       title = "Fig a: w/o TB, money needed for buying/storing/etc. equipment")

data%>%
  mutate(att_purtool = factor(att_purtool, levels = c("Strongly agree",
                                                "Agree",
                                                "Neutral", 
                                                "Disagree",
                                                "Strongly disagree", 
                                                 "N/A")))%>%  
  ggplot(aes(x=att_purtool, y=eco_totalcost))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(x="Agreement with TB reducing costs related to purchasing/renting tools/equipment",
       y= "Money",
       title = "Fig b: w/o TB, money needed for buying/storing/etc. equipment")

data%>%
  mutate(att_strtool = factor(att_strtool, levels = c("Strongly agree",
                                                "Agree",
                                                "Neutral", 
                                                "Disagree",
                                                "Strongly disagree", 
                                                 "N/A")))%>%  
  ggplot(aes(x=att_strtool, y=eco_totalcost))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(x="Agreement with TB reducing costs related to storing tools/equipment",
       y= "Money",
       title = "Fig c: w/o TB, money needed for buying/storing/etc. equipment")

data%>%
  mutate(att_redtime = factor(att_redtime, levels = c("Strongly agree",
                                                "Agree",
                                                "Neutral", 
                                                "Disagree",
                                                "Strongly disagree", 
                                                 "N/A")))%>%
  ggplot(aes(x=att_redtime, y=eco_totalcost))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(x="Agreement with TB reducing taff time for projects",
       y= "Money",
       title = "Fig d: w/o TB, money needed for buying/storing/etc. equipment")

data%>%
  mutate(att_evquality = factor(att_evquality, levels = c("Strongly agree",
                                                "Agree",
                                                "Neutral", 
                                                "Disagree",
                                                "Strongly disagree", 
                                                 "N/A")))%>%
  ggplot(aes(x=att_evquality, y=eco_totalcost))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(x="Agreement with TB increaing event quality",
       y= "Money",
       title = "Fig e: w/o TB, money needed for buying/storing/etc. equipment")
```


The following plots address the question of how savings vary by different Toolbank offerings

**Figures 24a-b: Money saved through TB (avg year) by Toolbank service**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
data%>%
  pivot_longer(eco_purchase:eco_maintain,names_to="service", values_to = "amount_saved")%>%
  mutate(`TB service` = case_when(service=="eco_purchase"~"purchasing/renting tools/equipment",
                                  service=="eco_storage"~"storing tools/equipment",
                                  service=="eco_maintain"~"maintaining tools/equipment"
                                  ))%>%
  ggplot(aes(x=`TB service`,y=amount_saved))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(y="amount saved in an average year",
       title= "Fig a: amount saved through TB services")

data%>%
  pivot_longer(eco_purchase:eco_maintain,names_to="service", values_to = "amount_saved")%>%
  mutate(`TB service` = case_when(service=="eco_purchase"~"purchasing/renting tools/equipment",
                                  service=="eco_storage"~"storing tools/equipment",
                                  service=="eco_maintain"~"maintaining tools/equipment"
                                  ))%>%
  filter(amount_saved<10000)%>%
  ggplot(aes(x=`TB service`,y=amount_saved))+
  geom_boxplot(color = "#265999", fill = "#93b9e1", linewidth = 1)+
  labs(y="amount saved in an average year",
       title= "Fig b: amount saved through TB services (zoomed in)")
```

The following information addresses the question of which types of events have TB tools and equipment helped the CBO to complete

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
sum_table = data.frame(choices = c("Quantity",
                                         "Quality",
                                         "Diversity",
                                         "Consistency",
                                         "other"),
                       Frequency  = round(c(nrow(data[data$ci_evimpact_qtt == 1,]),
                                            nrow(data[data$ci_evimpact_qlt == 1,]),
                                            nrow(data[data$ci_evimpact_dvt == 1,]),
                                            nrow(data[data$ci_evimpact_cst == 1,]),
                                            nrow(data[!is.na(data$ci_evimpact_otr),])),3),
                       Percentage = paste0(100*round(c(nrow(data[data$ci_evimpact_qtt == 1,])/nrow(data),
                                            nrow(data[data$ci_evimpact_qlt == 1,])/nrow(data),
                                            nrow(data[data$ci_evimpact_dvt == 1,])/nrow(data),
                                            nrow(data[data$ci_evimpact_cst == 1,])/nrow(data),
                                            nrow(data[!is.na(data$ci_evimpact_otr),])/nrow(data)),3), "%"))

sum_table[,-c(1)] %>% addHtmlTableStyle(col.columns = c("none", "#F7F7F7",
                                    "none", "#F7F7F7",
                                    "none", "#F7F7F7")) %>% 
  htmlTable(header =  c("# Respondents", "% Respondents"),
            rnames = c("Quantity",
                       "Quality",
                       "Diversity",
                       "Consistency",
                       "Other"),
            rgroup = c("Choice*"),
            n.rgroup = c(5),
            caption = "Table 6: Ways community events would be impact without TB")
```

**Figure 25: Percentage for Ways Events Got Impacted without TB**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
sum_table2 = data.frame(choices = c("Quantity",
                                         "Quality",
                                         "Diversity",
                                         "Consistency",
                                         "other"),
                       Frequency  = round(c(nrow(data[data$ci_evimpact_qtt == 1,]),
                                            nrow(data[data$ci_evimpact_qlt == 1,]),
                                            nrow(data[data$ci_evimpact_dvt == 1,]),
                                            nrow(data[data$ci_evimpact_cst == 1,]),
                                            nrow(data[!is.na(data$ci_evimpact_otr),])),3),
                       percentage = 100*round(c(nrow(data[data$ci_evimpact_qtt == 1,])/nrow(data),
                                            nrow(data[data$ci_evimpact_qlt == 1,])/nrow(data),
                                            nrow(data[data$ci_evimpact_dvt == 1,])/nrow(data),
                                            nrow(data[data$ci_evimpact_cst == 1,])/nrow(data),
                                            nrow(data[!is.na(data$ci_evimpact_otr),])/nrow(data)),3))

ggplot(sum_table2)+
  geom_bar(aes(x = choices, y = percentage), stat='identity', fill = "#265999") +
  labs(x = "ways events impacted without TB", y = "percentage responded", title = NULL) +
  ylim(c(0,100))
```


```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
sum_table = data.frame(choices = c("Fundraising",
                                         "Service Projects",
                                         "Educational Workshops",
                                         "Community Building",
                                         "other"),
                       Frequency = round(c(nrow(data[data$eve_type_fr == 1,]),
                                            nrow(data[data$eve_type_sp == 1,]),
                                            nrow(data[data$eve_type_ew == 1,]),
                                            nrow(data[data$eve_type_cb == 1,]),
                                            nrow(data[!is.na(data$eve_type_otr),])),3),
                       Percentage = paste0(100*round(c(nrow(data[data$eve_type_fr == 1,])/nrow(data),
                                            nrow(data[data$eve_type_sp == 1,])/nrow(data),
                                            nrow(data[data$eve_type_ew == 1,])/nrow(data),
                                            nrow(data[data$eve_type_cb == 1,])/nrow(data),
                                            nrow(data[!is.na(data$eve_type_otr),])/nrow(data)),3), "%"))
sum_table[, -c(1)] %>% addHtmlTableStyle(col.columns = c("none", "#F7F7F7",
                                    "none", "#F7F7F7",
                                    "none", "#F7F7F7")) %>% 
  htmlTable(header =  c("# Respondents", "% Respondents"),
            rnames = c("Fundraising",
                       "Service Projects",
                       "Educational Workshops",
                       "Community Building",
                       "Other"),
            rgroup = c("Choice*"),
            n.rgroup = c(5),
            caption = "Table 7: Events types TB helped to complete")
```


**Figure 27: Percentage for Event Types TB helps to Complete**

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
sum_table2 = data.frame(choices = c("Fundraising",
                                         "Service Projects",
                                         "Educational Workshops",
                                         "Community Building",
                                         "other"),
                       Frequency = round(c(nrow(data[data$eve_type_fr == 1,]),
                                            nrow(data[data$eve_type_sp == 1,]),
                                            nrow(data[data$eve_type_ew == 1,]),
                                            nrow(data[data$eve_type_cb == 1,]),
                                            nrow(data[!is.na(data$eve_type_otr),])),3),
                       percentage = 100*round(c(nrow(data[data$eve_type_fr == 1,])/nrow(data),
                                            nrow(data[data$eve_type_sp == 1,])/nrow(data),
                                            nrow(data[data$eve_type_ew == 1,])/nrow(data),
                                            nrow(data[data$eve_type_cb == 1,])/nrow(data),
                                            nrow(data[!is.na(data$eve_type_otr),])/nrow(data)),3))

ggplot(sum_table2)+
  geom_bar(aes(x = choices, y = percentage), stat='identity', fill = "#265999") +
  labs(x = "Event Types TB Tools Support", y = "percentage responded", title = NULL) +
  ylim(c(0,100))

```

**Findings:**

- Respondents with more positive attitudes with the ToolBank helping reduce their costs in multiple aspects would have spent more on buying, storing and maintaining tools or equipment if the ToolBank did not exist (not statistically significant)
- The ToolBank helps to save the most in purchasing tools and equipment than storing and maintaining those (not statistically significant)
- Events got impacted by the TB mainly through their quality (77.8%), consistency (66.7%), and quantity (55.6%)
- The most prominent types of events the Toolbank supports are community building (84.4%) and service projects (75.6%)



The following information addresses the question of what percent of the event expense budget was saved by using TB equipment.

```{r,out.width="50%",fig.show="hold",warning=FALSE,message=FALSE,echo=FALSE}
sum_table = cbind(mean = round(mean(data$eve_fundraise_p, na.rm = T),1),
                  q25 = quantile(data$eve_fundraise_p, na.rm = T, 0.25),
                  median = median(data$eve_fundraise_p, na.rm = T),
                  mode = Mode(data$eve_fundraise_p),
                  q75 = quantile(data$eve_fundraise_p, na.rm = T, 0.75),
                  sd = round(sd(data$eve_fundraise_p, na.rm = T),1))


sum_table%>% 
  addHtmlTableStyle(col.columns = c("none", "#F7F7F7",
                                    "none", "#F7F7F7",
                                    "none", "#F7F7F7"))%>% 
  htmlTable(header =  c("Mean","25th quantile", "Median", "Mode","75th quantile","Standard deviation"),
            rnames = c("% of event expense budget"),
            caption = "Table 8: Event expense budget saved by using TB equipment")
```

**Findings:**

- Half of the respondents reported that using the ToolBank helped their CBO save at least 30% of their event expense budget.


